### 2023-09-06 Paper/main.tex
add paper

\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{hyperref}
\usepackage{listings}
\begin{document}

\section{Encoding Software}

To encode the loss less images into the respective codec for the experiment, several encoder where used. 
\subsection{AVIF, JPEG and WebP}
For those encoders the python package pillow-avif-plugin and pillow was used. The additional pillow plugin can be installed via pip install pillow-avif-plugin. To encode a lossless image, the image is opened and save with a specific quality as seen in \ref{avif_1}. The quality parameter ranges from 1(lowest) to 100(highest). It is important to set the specific file extension for the software to 
know in which codec the image needs to be encoded.
\begin{lstlisting}[label={avif_1}, language=Python, caption=Encode AVIF\, JPEG and WebP]
image = Image.open(image_path)
image.save(outputPath, quality=q)
\end{lstlisting}

\subsection{BPG}
To encode the images in BPG the Linux distribution from Fabrice Bellard's website (https://bellard.org/bpg/) was used. As seen in \ref{bpg_1} the output path is given after the -o argument and the specific quality after the -q argument. The quality parameter ranges from 51(lowest) to 0(highest). The last argument that needs no specific indicator is the original image.

\begin{lstlisting}[label={bpg_1}, language=Python, caption=Encode BPG]
os.system('bpgenc -o ' + outputPath + \
    ' -q ' + str(int(maxQ - q)) + \
    ' ' + image_path)
\end{lstlisting}

\subsection{HEIC}
Same as with the AVIF codec HEIC is also supported in a python package. For this codec the package pillow\_heif which can be installed with pip pillow-heif. The quality parameter ranges from 1(lowest) to 100(highest).
How the image can be encoded in HEIC is shown in \ref{heic_1}.

\begin{lstlisting}[label={heic_1}, language=Python, caption=Encode HEIC]
image = pillow_heif.from_pillow(Image.open(image_path))
image.save(outputPath, quality=q)
\end{lstlisting}

\subsection{JPEG2000}
For the JPEG standards JPEG itself provides software to encode images. In the experiment the libopenjp2 was used. This library is in the Linux package manager and can be installed with apt-get install libopenjp2-tools. The quality parameter which ranges from 1(lowest) to 1000(highest) is given to the software with the -r parameter. An example how this can be done in Python is shown in \ref{jpeg2k_1}.
\begin{lstlisting}[label={jpeg2k_1}, language=Python, caption=Encode JPEG 2000]
subprocess.call('opj_compress -o ' + outputPath + \
                ' -r ' + str(int(maxQ - q)) + \
                ' -i ' + image_path,
                stdout=subprocess.DEVNULL,
                stderr=subprocess.DEVNULL,
                shell=True)
\end{lstlisting}

\subsection{JXL}
For JPEG XL the JPEG organization also provides a package which can be installed in Linux. For that encoder the libjxl (apt install libjxl-devtools) was used. The quality parameter ranges from 1(lowest) to 100 (highest) and an example to encode a image is shown in \ref{jxl_1}
\begin{lstlisting}[label={jxl_1}, language=Python, caption=Encode JPEG XL]
subprocess.call(['cjxl', image_path, outputPath, 
                 '--quiet', '-q', str(q)])
\end{lstlisting}
\subsection{JXR}
For JXR the package libjxr-devtools was used. This includes a specific encoder and decoder app. The quality ranges from 0(lowest) to 1(highest). Here floating point numbers need to be used for quality.
An example how to encode a image with jxr is shown in \ref{jxr_1}. In addition to the quality parameter jxr also support quantization, although this results in very good compression rate, the image quality is affected drastically. 
\begin{lstlisting}[label={jxr_1}, language=Python, caption=Encode BPG]
os.system('JxrEncApp -q ' + q_str + \
            ' -o ' + output_path + \
            ' -i ' + tif_path)
\end{lstlisting}

\newpage
\section{michi filesize}
\label{sec: filesize}
\newpage

\section{RESNET explanation (Stef)}

\subsection{Training without transfer learning}

The idea behind training the network from scratch is that the network would be mor tailored to the given task since it has no previous information stored in the network. This contrasts with transfer learning since there prior information is present.
\newline

\noindent
\textbf{Dataset Details:}

\noindent
To train the network the DIV2K training and validation Dataset was used. The dataset contains 800 train images and 100 test images. Since the images had different dimensions, we first had to crop them to specific in this case 512x512. Afterwards we compressed the images to specified file sizes as described in \ref{sec: filesize}. This leads to 10 classes – one for each compression algorithm – for each file size category. We trained the network by using the images that were compressed to a file size of 25kB.
\newline

\noindent
\textbf{Training Details:}

\noindent
For the self-trained network, we used an Adam Optimizer with a learning rate of 1e-4 and a weight decay of 1e-4. As a loss function Cross entropy was used. To be able to match the output of the network to the 10 classes used we replaced the final fully connected layer in the Resnet architecture with one that outputs the 10 codec classes.

\noindent
In the first iteration we trained the network on the original cropped 800 images per class. This leads to 8000 images available for the network to train. With that amount there was little progress during the first epochs. To be able to train on a larger dataset we then cropped the corners of each image to 512x512 to get 5x the number of usable images. This lead to 4000 images per class for the network to train.

\noindent
After 10 epochs of training, we achieved a validation accuracy of 57,6 percent. For 10 epochs this is lower than the results we got for the transfer learning approach. However, if one would increase the number of epochs, we expect to reach the same levels of accuracy since the only defencemen is that the pretrained network has a preferable starting position compared to the one without transfer learning. This can be shown by changing the starting seed to something different leading to only 10 percent accuracy after 10 epochs.

\subsection{Transferlearning}
For this approach the ResNet18 model was used as a baseline. To adjust this pre trained model for the requirements of the experiment, the output layers where reconfigured to represent the 8 different codecs in which the images where encoded.
In addition the model uses just 224x224 images as inputs, thus the encoded images where center cropped to fit that size.

\noindent
Then the model was trained over 10 epochs on 4000 test images. The learning rate was set to 0.001 with a momentum of 0.9 due to the model being already trained on a huge data set and in the experiment just the adjustment for the codec artifacts should be added. For the whole implementation see appendix.

\section{Results}
\label{Results}
A mixed model was developed by training the model with images of filesizes 5, 10, 17, 25 and 32. This resulted in 4500 images (512x512) for each codec. The considered dataset has only 900 images. To compare the filesize models with the mixed model, the filesize models need the same amount of input images as the mixed model. Therefore, each image of the dataset was cropped into five images to get an amount of 4500 images for the training and testing.

\section{Performance}
For the classification each model was evaluated with each filesize. The result is represented in the figure \ref{fig: acc_comparison}.

\begin{figure}[h!]
	\centering
	\includegraphics[width=12cm]{accuracy_comparison.png}
	\caption{Accuracy Comparison}
	\label{fig: acc_comparison}
\end{figure}

\noindent
The self trained model showed an accuracy over all filesizes of 10 percent. With ten different codecs, random guessing would lead to the same result as this model. For the self trained model 40000 images where used. The pretrained model was already trained on 1,2 million images. Therefore, the self trained model would need much more images to get a better performance. With only 2400 images used for training, this model represents the worst model for the classification task.

\noindent
The models trained with the filesizes 60, 75 and 100 have a low accuracy for small filesizes and increase for bigger filesizes. Small filesize images have more artifacts, which are not taken into account in this models. For that reason the models of 60, 75 and 100 filesize could only be used to classify codecs with the same filesizes.

\noindent
The smaller filesize models have their peaks arround the filesizes they were trained on. However, for the images with less than 40kB this models have an accuracy of about 95 percent. For the bigger filesizes the accuracy is decreasing. The bigger filesizes have less artifacts in the images and also many codecs get the maximum quality after 60kB, which explains the decrease of accuracy for this models.

\noindent
An assumtion was that the mixed model would lead to the best result because of considering different filesizes for the model. As the figure \ref{fig: acc_comparison} shows, almost every small filesize model has a better performance than the mixed model.

\noindent
For classifying images with the given filesizes the model trained with 40kB would lead to the best result. However, for smaller filesize images (\textless 50kB) the model trained with 32kB images would be the right choice because of the bigger accuracy for 5kB images.

\section{Loss function}

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.7\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{loss_comparison_filesize_10.png}
        \caption{Loss of model with filesize 10}
        \label{fig:loss_comparison_filesize_10}
    \end{minipage}\hfill
    \begin{minipage}{0.7\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{loss_comparison_mixed.png}
        \caption{Loss of mixed model}
        \label{fig:loss_comparison_filesize_mixed}
    \end{minipage}
\end{figure}

\noindent
In the figure \ref{fig:loss_comparison_filesize_10} and \ref{fig:loss_comparison_filesize_mixed} the loss over ten epochs is represented. After 10 epochs the loss is already minimal, therefore further training would not make a significant change. The other nine models show a similar behavior as figure \ref{fig:loss_comparison_filesize_10} shows.

\end{document}

### 2023-09-07 Paper/main.tex
Add archived filesize section

@@
 \section{Encoding Software}
+\label{sec: encoder}
 
@@
 \newpage
-\section{michi filesize}
+\section{Achieving Fixed Filesize Compression Through Binary Search Algorithm}
 \label{sec: filesize}
+
+The primary objective was to attain a consistent and fixed filesize for the encoder discussed in chapter \ref{sec: encoder}.
+To achieve this goal efficiently, we devised a binary search algorithm, strategically designed to conserve computational resources and time.
+This algorithm, when coupled with the encoders enabled us to successfully compress the original images while maintaining a specified filesize.
+The results are graphically represented in image \ref{fig: fsize_comparison}, which displays boxplots illustrating the distribution of the encoder performances for targeting file size 32kB.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=8cm]{filesize_comparison.png}
+	\caption{Archived filesizes for used encoder}
+	\label{fig: fsize_comparison}
+\end{figure}
+
+\noindent
+To ensure the proper functioning of the employed encoder, we conducted calculations of Peak Signal to Noise Ratio (PSNR) and generated plots depicting its relationship with the achieved compression rates.
+To maintain clarity in the plots, we utilized JPEGXR with its default overlapping parameter (1).
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=8cm]{psnr.png}
+	\caption{PSNR comparison of the used codecs}
+	\label{fig: psnr_comparison}
+\end{figure}
+
+\noindent
+As anticipated, the results presented in plot \ref{fig: psnr_comparison} affirm that the plain JPEG encoder consistently yields in reduced-quality images when operating at lower compression rates.
+The driving motivation behind this attempt was to intentionally introduce diverse encoding artifacts into the compressed images for later train a model and classify the used image encoder.
 \newpage

### 2023-09-07 Paper/main.tex
Fix typos

@@
 \usepackage{hyperref}
+\hypersetup{
+    colorlinks=true, % Set this to true to remove the border
+    linkcolor=black, % Color for internal links
+    citecolor=black, % Color for citations
+    }
 \usepackage{listings}
+\usepackage{blindtext}
+\usepackage{geometry}
+\geometry{margin=25mm}
 \begin{document}
@@
 The additional pillow plugin can be installed via pip install pillow-avif-plugin.
-To encode a lossless image, the image is opened and save with a specific quality as seen in \ref{avif_1}.
+To encode a lossless image, the image is opened and save with a specific quality as seen in listing \ref{avif_1}.
 The quality parameter ranges from 1(lowest) to 100(highest).
@@
 To encode the images in BPG the Linux distribution from Fabrice Bellard's website (https://bellard.org/bpg/) was used.
-As seen in \ref{bpg_1} the output path is given after the -o argument and the specific quality after the -q argument.
+As seen in listing \ref{bpg_1} the output path is given after the -o argument and the specific quality after the -q argument.
 The quality parameter ranges from 51(lowest) to 0(highest).
@@
 The quality parameter ranges from 1(lowest) to 100(highest).
-How the image can be encoded in HEIC is shown in \ref{heic_1}.
+How the image can be encoded in HEIC is shown in listing \ref{heic_1}.
 
@@
 The quality parameter which ranges from 1(lowest) to 1000(highest) is given to the software with the -r parameter.
-An example how this can be done in Python is shown in \ref{jpeg2k_1}.
+An example how this can be done in Python is shown in listing \ref{jpeg2k_1}.
 \begin{lstlisting}[label={jpeg2k_1}, language=Python, caption=Encode JPEG 2000]
@@
 
-\section{RESNET explanation (Stef)}
+\section{RESNET explanation}
 
@@
 
-The idea behind training the network from scratch is that the network would be mor tailored to the given task since it has no previous information stored in the network.
+The idea behind training the network from scratch is that the network would be more tailored to the given task since it has no previous information stored in the network.
 This contrasts with transfer learning since there prior information is present.
@@
 \noindent
-To train the network the DIV2K training and validation Dataset was used.
+To train the network the DIV2K training and validation dataset was used.
 The dataset contains 800 train images and 100 test images.
@@
 For this approach the ResNet18 model was used as a baseline.
-To adjust this pre trained model for the requirements of the experiment, the output layers where reconfigured to represent the 8 different codecs in which the images where encoded.
+To adjust this pretrained model for the requirements of the experiment, the output layers where reconfigured to represent the 8 different codecs in which the images where encoded.
 In addition the model uses just 224x224 images as inputs, thus the encoded images where center cropped to fit that size.
@@
 \noindent
-The smaller filesize models have their peaks arround the filesizes they were trained on.
+The smaller filesize models have their peaks around the filesizes they were trained on.
 However, for the images with less than 40kB this models have an accuracy of about 95 percent.

### 2023-09-07 Paper/main.tex
Add ResNet description with bibliography link

@@
 \section{RESNET explanation}
+Residual Networks are deep learning models, that where developed by Kaiming He, Xiangyu Zhang, Shaoqing Ren, and Jian Sun.
+This networks enable easier training of deep learning models.
+For an explicit explanation on how a ResNet works see \cite{he2015deep}.
+
+@misc{he2015deep,
+      title={Deep Residual Learning for Image Recognition}, 
+      author={Kaiming He and Xiangyu Zhang and Shaoqing Ren and Jian Sun},
+      year={2015},
+      eprint={1512.03385},
+      archivePrefix={arXiv},
+      primaryClass={cs.CV}
+}
 

### 2023-09-07 scripts/evaluateMixedModel_withoutTransfer.py
Add Plots

@@ -1,0 +1,92 @@
+import torch
+from sklearn.metrics import precision_recall_fscore_support
+from torch import nn
+from torchvision import transforms, models
+import numpy as np
+from matplotlib import pyplot as plt
+
+import cnnDataset
+
+
+def evaluate_model(model, test_loader):
+    device = (
+        "cuda"
+        if torch.cuda.is_available()
+        else "mps"
+        if torch.backends.mps.is_available()
+        else "cpu"
+    )
+
+    model.to(device)
+    model.eval()
+    correct = 0
+    total = 0
+    all_preds = []
+    all_labels = []
+
+    with torch.no_grad():
+        for images, labels in test_loader:
+            images, labels = images.to(device), labels.to(device)
+
+            outputs = model(images)
+            #L2 normalization of the output
+            prediction = np.sqrt(np.sum(np.square(outputs.cpu().numpy()), axis=1))
+            prediction = np.sqrt(np.sum(np.square(prediction), axis=0))
+            total += labels.size(0)  # Update the total count of processed samples
+
+            all_preds.append(prediction)
+            all_labels.extend(labels.cpu().numpy())
+
+    #scatter plot all_preds color coded by all_labels
+    
+    plt.scatter(all_preds,range(len(all_preds)))
+    plt.show()
+    plt.savefig('results/scatter_plot_withoutTrain.png')
+
+
+    return 
+
+
+def main():
+    #filesizes = ['5', '10', '17', '25', '32', '40', '50', '60', '75', '100']
+    filesizes = ['5']
+
+    result_dictionary = {
+        '5': 0,
+        '10': 0,
+        '17': 0,
+        '25': 0,
+        '32': 0,
+        '40': 0,
+        '50': 0,
+        '60': 0,
+        '75': 0,
+        '100': 0
+    }
+
+    for filesize in filesizes:
+        transform = transforms.Compose([
+            # the model excepts just 224x224 images, maybe we need to crop our images before encoding them
+            # I used crop, resize would change the image and therefore can lead to probles for our classification
+            transforms.CenterCrop(224),
+            transforms.ToTensor(),
+            transforms.Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225]),
+        ])
+
+        _, val_loader = cnnDataset.create_dataset(transform=transform, filesize=filesize)
+
+        model_name = 'resnet18'
+        model = models.resnet18()
[…]

### 2023-09-07 scripts/plotResults.py

@@ -86,34 +86,27 @@ def plot_filesize_to_target():
     #read csv
     df = pd.read_csv('filesize_log.txt', sep=',', header=None)
     df.columns = ['filesize', 'target', 'codec']
-    print(df.head())
-    #split dataframes into each codec
-    df_avif = df[df['codec'] == ' AVIF/']
-    df_webp = df[df['codec'] == ' WebP/']
-    df_bpg = df[df['codec'] == ' BPG/']
-    df_heic = df[df['codec'] == ' HEIC/']
-    df_jxl = df[df['codec'] == ' JPEG_XL/']
-    df_jxr = df[df['codec'] == ' JPEG_XR/']
-    df_jpeg2000 = df[df['codec'] == ' JPEG_2000/']
-    df_jpeg = df[df['codec'] == ' JPEG/']
+    #sort by string in codec column and reset index
+    df = df.sort_values(by=['codec']).reset_index(drop=True)
+    #remove / from codec column
+    df['codec'] = df['codec'].str.replace('/', '')
     #scatter plot with each codec in different color with filesize as y and index as x
     plt.figure(figsize=(20, 10))
-    plt.scatter(df_avif.index, df_avif['filesize'], c='r', label='AVIF')
-    plt.scatter(df_webp.index, df_webp['filesize'], c='g', label='WebP')
-    plt.scatter(df_bpg.index, df_bpg['filesize'], c='b', label='BPG')
-    plt.scatter(df_heic.index, df_heic['filesize'], c='y', label='HEIC')
-    plt.scatter(df_jxl.index, df_jxl['filesize'], c='c', label='JPEG XL')
-    plt.scatter(df_jxr.index, df_jxr['filesize'], c='m', label='JPEG XR')
-    plt.scatter(df_jpeg2000.index, df_jpeg2000['filesize'], c='k', label='JPEG 2000')
-    plt.scatter(df_jpeg.index, df_jpeg['filesize'], c='orange', label='JPEG')
+    #plt df with a color for each codec
+    label = df['codec'].unique()
+    #box plot
+    plot = plt.boxplot([df[df['codec'] == label]['filesize'] for label in label], labels=label)    
+    
+    #for i, label in enumerate(label):
+    #    plt.scatter(df[df['codec'] == label].index, df[df['codec'] == label]['filesize'], label=label)
     #plot line at target value
-    plt.axhline(y=32, color='black', linestyle='--', label='Target')
-    plt.ylim(0, 35)
[…]

### 2023-09-07 scripts/pretrainedCNN.py

@@ -5,7 +5,7 @@ import torch.optim as optim
 from torchvision import transforms, models
 from sklearn.metrics import precision_recall_fscore_support
 import cnnDataset
-import evaluateMixedModel
+import scripts.evaluateMixedModel_withoutTransfer as evaluateMixedModel_withoutTransfer
 
 #TODO: Log the output in a file
 
@@ -124,4 +124,4 @@ if save_model:
     torch.save(model.state_dict(), "models/cnnParams_" + model_name + ".pt")
     print("Model saved")
 
-evaluateMixedModel.main()
+evaluateMixedModel_withoutTransfer.main()

### 2023-09-07 Paper/main.tex
Add BibTex stuff

@@
+\begin{filecontents}{shortbib.bib}
+@misc{he2015deep,
+      title={Deep Residual Learning for Image Recognition}, 
+      author={Kaiming He and Xiangyu Zhang and Shaoqing Ren and Jian Sun},
+      year={2015},
+      eprint={1512.03385},
+      archivePrefix={arXiv},
+      primaryClass={cs.CV}
+}
+\end{filecontents}
+
 \documentclass{article}
 \usepackage{graphicx} % Required for inserting images
+\usepackage{biblatex}
+\bibliography{shortbib}
 \usepackage{hyperref}
@@
 
-@misc{he2015deep,
-      title={Deep Residual Learning for Image Recognition}, 
-      author={Kaiming He and Xiangyu Zhang and Shaoqing Ren and Jian Sun},
-      year={2015},
-      eprint={1512.03385},
-      archivePrefix={arXiv},
-      primaryClass={cs.CV}
-}
-
 \subsection{Training without transfer learning}

### 2023-09-07 Paper/main.tex
Add bibliography at bottom
Adapt filesize comparison plot size
Add SSIM metric (#70)

@@
 \documentclass{article}
+\usepackage[a4paper, margin=1in]{geometry}
 \usepackage{graphicx} % Required for inserting images
@@
 \usepackage{blindtext}
-\usepackage{geometry}
+\usepackage{cleveref}
+\usepackage{subcaption}
 \geometry{margin=25mm}
@@
 	\centering
-	\includegraphics[width=8cm]{filesize_comparison.png}
+	\includegraphics[width=12cm]{filesize_comparison.png}
 	\caption{Archived filesizes for used encoder}
@@
 \noindent
-To ensure the proper functioning of the employed encoder, we conducted calculations of Peak Signal to Noise Ratio (PSNR) and generated plots depicting its relationship with the achieved compression rates.
-To maintain clarity in the plots, we utilized JPEGXR with its default overlapping parameter (1).
+To validate the performance of the utilized encoder, we carried out assessments involving two key metrics: Peak Signal to Noise Ratio (PSNR) and Structural Similarity Index (SSIM).
+Both metrics got calculated as mean values over 5 images.
+These evaluations were displayed in plot \ref{fig: comparison} to generate graphical representations illustrating the correlation between these metrics and the resultant compression rates.
+To ensure visual clarity within the plots, we employed the JPEGXR compression algorithm with its default overlapping parameter set to 1.
 
@@
     \centering
-	\includegraphics[width=8cm]{psnr.png}
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{psnr.png}
           \caption{PSNR comparison of the used codecs}
           \label{fig: psnr_comparison}
+      \end{subfigure}
+      \hfill
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{ssim.png}
+          \caption{SSIM comparison of the used codecs}
+          \label{fig:CI}
+      \end{subfigure}
+\caption{
+\label{fig: comparison}%
+Comparison of PSNR and SSIM}
 \end{figure}
@@
 \noindent
-As anticipated, the results presented in plot \ref{fig: psnr_comparison} affirm that the plain JPEG encoder consistently yields in reduced-quality images when operating at lower compression rates.
+As anticipated, the results presented in plot \ref{fig: comparison} affirm that the plain JPEG encoder consistently yields in reduced-quality images when operating at lower compression rates.
 The driving motivation behind this attempt was to intentionally introduce diverse encoding artifacts into the compressed images for later train a model and classify the used image encoder.
@@
 
+\printbibliography
 \end{document}

### 2023-11-25 Paper/main.tex
Fix image path and update training details

@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{ssim.png}
+        \includegraphics[width=\textwidth]{../Plots/ssim.png}
           \caption{SSIM comparison of the used codecs}
@@
 This contrasts with transfer learning since there prior information is present.
+As a model the ResNet18 architecture was used.
+This architecture was chosen since it is a good compromise between network size and performance.
 \newline
@@
 Afterwards we compressed the images to specified file sizes as described in \ref{sec: filesize}.
-This leads to 10 classes – one for each compression algorithm – for each file size category.
-We trained the network by using the images that were compressed to a file size of 25kB.
-\newline
+With the primary objectice beeing to recignize the different compression algorithms the output of the network should represent the different encoding schemes.
+This leads to 10 classes in each file size category.
 
@@
 \noindent
-After 10 epochs of training, we achieved a validation accuracy of 57,6 percent.
+After 10 epochs of training, we achieved a validation accuracy of 57,6 percent avaged over the 5 training filesizes (5, 10, 17, 25 and 32).
 For 10 epochs this is lower than the results we got for the transfer learning approach.
@@
 \subsection{Transferlearning}
-For this approach the ResNet18 model was used as a baseline.
-To adjust this pretrained model for the requirements of the experiment, the output layers where reconfigured to represent the 8 different codecs in which the images where encoded.
+To be able to compare the results of the self-trained model with a pretrained model, the ResNet18 architecture was used again.
+The pretrained model was already trained on 1,2 million images to give an preferable starting position for training.
+To adjust this pretrained model for the requirements of the experiment, the output layers where reconfigured to represent the 10 different codecs in which the images where encoded.
 In addition the model uses just 224x224 images as inputs, thus the encoded images where center cropped to fit that size.
@@
 \noindent
-The self trained model showed an accuracy over all filesizes of 10 percent.
-With ten different codecs, random guessing would lead to the same result as this model.
-For the self trained model 40000 images where used.
-The pretrained model was already trained on 1,2 million images.
-Therefore, the self trained model would need much more images to get a better performance.
-With only 2400 images used for training, this model represents the worst model for the classification task.
+The self trained model was trained with the filesizes 5, 10, 17, 25 and 32 on all 10 codecs.
+This leads to 4000 images for each codec per epoch.
+As one can see in figure \ref{fig: acc_comparison} the self trained model has its best performances at filesizes 10, 17 and 25 ranging from 62 to 65 percent accuracy.
 

### 2023-11-28 scripts/jxrenc_0.py
change plots to pgf

@@ -2,6 +2,7 @@ import os
 import glob
 import numpy as np
 from PIL import Image
+from filesizelogger import log_filesize
 
 minQ = 1
 # to increase the floating point precision this high value is needed (q needs to be in range 0-1)
@@ -118,6 +119,7 @@ def encode_jxr(printProgress=False, maxFileSizeKb=32, useMultiCropPerImage=False
                 f_size = os.path.getsize(outputPath) / 1024
                 i += 1
                 print('Image: ' + file_name + ' Quality: ' + str(q) + ' Filesize: ' + str(f_size) + ' kb' + ' Progress: ' + str(i) + '/' + str(number_of_files))
+                log_filesize(f_size, maxFileSizeKb, usedCodec)
 
             dec_file_name = file_name.split(sep='.')[0] + '_' + str(maxFileSizeKb) + tifFileExtension
             dec_path = pathImagesEncoded[:-len(usedCodec)] + decodedFolder + str(maxFileSizeKb)+ "/" + usedCodec + dec_file_name

### 2023-11-28 scripts/jxrenc_2.py

@@ -2,6 +2,7 @@ import os
 import glob
 import numpy as np
 from PIL import Image
+from filesizelogger import log_filesize
 
 minQ = 1
 # to increase the floating point precision this high value is needed (q needs to be in range 0-1)
@@ -114,6 +115,7 @@ def encode_jxr(printProgress=False, maxFileSizeKb=32, useMultiCropPerImage=False
                 f_size = os.path.getsize(outputPath) / 1024
                 i += 1
                 print('Image: ' + file_name + ' Quality: ' + str(q) + ' Filesize: ' + str(f_size) + ' kb' + ' Progress: ' + str(i) + '/' + str(number_of_files))
+                log_filesize(f_size, maxFileSizeKb, usedCodec)
 
             dec_file_name = file_name.split(sep='.')[0] + '_' + str(maxFileSizeKb) + tifFileExtension
             dec_path = pathImagesEncoded[:-len(usedCodec)] + decodedFolder + str(maxFileSizeKb)+ "/" + usedCodec + dec_file_name

### 2023-11-28 scripts/preprocessing.py

@@ -27,16 +27,16 @@ async def preprocess(cropNeeded=False,
     print('Start to encode images.')
     with ThreadPoolExecutor() as executor:
         futures = [
-            executor.submit(avifenc.encode_avif, printProgress, maxFileSizeKb),
-            executor.submit(bpgenc.encode_bpg, printProgress, maxFileSizeKb),
-            executor.submit(heicEnc.encode_heic, printProgress, maxFileSizeKb),
+            #executor.submit(avifenc.encode_avif, printProgress, maxFileSizeKb),
+            #executor.submit(bpgenc.encode_bpg, printProgress, maxFileSizeKb),
+            #executor.submit(heicEnc.encode_heic, printProgress, maxFileSizeKb),
             executor.submit(jxrenc_0.encode_jxr, printProgress, maxFileSizeKb),
             executor.submit(jxrenc_1.encode_jxr, printProgress, maxFileSizeKb),
             executor.submit(jxrenc_2.encode_jxr, printProgress, maxFileSizeKb),
-            executor.submit(webP.encode_webp, printProgress, maxFileSizeKb),
-            executor.submit(jpegxl.encode_jpgxl, printProgress, maxFileSizeKb),
-            executor.submit(jpeg2000enc.encode_jpeg2k, printProgress, maxFileSizeKb),
-            executor.submit(jpegenc.encode_jpeg, printProgress, maxFileSizeKb),
+            #executor.submit(webP.encode_webp, printProgress, maxFileSizeKb),
+            #executor.submit(jpegxl.encode_jpgxl, printProgress, maxFileSizeKb),
+            #executor.submit(jpeg2000enc.encode_jpeg2k, printProgress, maxFileSizeKb),
+            #executor.submit(jpegenc.encode_jpeg, printProgress, maxFileSizeKb),
         ]
         for future in futures:
             future.result()
@@ -44,8 +44,8 @@ async def preprocess(cropNeeded=False,
 
 
 if __name__ == '__main__':
-    #filesizes = [5, 10, 17, 25, 32, 40, 50, 60, 75, 100]
-    filesizes = [10]
+    filesizes = [5, 10, 17, 25, 32, 40, 50, 60, 75, 100]
+    #filesizes = [5]
     for filesize in filesizes:
         asyncio.run(preprocess(maxFileSizeKb=filesize))
    

### 2023-11-28 scripts/quality.py

@@ -11,6 +11,16 @@ pillow_heif.register_heif_opener()
 
 import cv2
 import matplotlib.pyplot as plt
+import matplotlib
+#Make matplotlib use latex for font rendering
+matplotlib.use("pgf")
+matplotlib.rcParams.update({
+    "pgf.texsystem": "pdflatex",
+    'font.family': 'serif',
+    'text.usetex': True,
+    'pgf.rcfonts': False,
+})
+
 import numpy as np
 from PIL import Image
 
@@ -182,7 +192,7 @@ def _plot_results(codecs, results, metric, save_path):
     plt.xlim((4, 100))
     plt.xlabel('Compression Rate')
     plt.ylabel(metric)
-    plt.savefig(save_path)
+    plt.savefig(save_path+'.pgf')
     plt.close()
 
 
@@ -192,8 +202,8 @@ def plot_results():
     ssim_results = np.load('results/results_quality_ssim.npy', allow_pickle=True).item()
     codecs = psnr_results.keys()
 
-    _plot_results(codecs, psnr_results, 'PSNR', 'Plots/psnr.png')
-    _plot_results(codecs, ssim_results, 'SSIM', 'Plots/ssim.png')
+    _plot_results(codecs, psnr_results, 'PSNR', 'Plots/psnr')
+    _plot_results(codecs, ssim_results, 'SSIM', 'Plots/ssim')
 
 
 if __name__ == '__main__':

### 2023-11-28 scripts/preprocessing.py
remove comments

@@ -27,16 +27,16 @@ async def preprocess(cropNeeded=False,
     print('Start to encode images.')
     with ThreadPoolExecutor() as executor:
         futures = [
-            #executor.submit(avifenc.encode_avif, printProgress, maxFileSizeKb),
-            #executor.submit(bpgenc.encode_bpg, printProgress, maxFileSizeKb),
-            #executor.submit(heicEnc.encode_heic, printProgress, maxFileSizeKb),
+            executor.submit(avifenc.encode_avif, printProgress, maxFileSizeKb),
+            executor.submit(bpgenc.encode_bpg, printProgress, maxFileSizeKb),
+            executor.submit(heicEnc.encode_heic, printProgress, maxFileSizeKb),
             executor.submit(jxrenc_0.encode_jxr, printProgress, maxFileSizeKb),
             executor.submit(jxrenc_1.encode_jxr, printProgress, maxFileSizeKb),
             executor.submit(jxrenc_2.encode_jxr, printProgress, maxFileSizeKb),
-            #executor.submit(webP.encode_webp, printProgress, maxFileSizeKb),
-            #executor.submit(jpegxl.encode_jpgxl, printProgress, maxFileSizeKb),
-            #executor.submit(jpeg2000enc.encode_jpeg2k, printProgress, maxFileSizeKb),
-            #executor.submit(jpegenc.encode_jpeg, printProgress, maxFileSizeKb),
+            executor.submit(webP.encode_webp, printProgress, maxFileSizeKb),
+            executor.submit(jpegxl.encode_jpgxl, printProgress, maxFileSizeKb),
+            executor.submit(jpeg2000enc.encode_jpeg2k, printProgress, maxFileSizeKb),
+            executor.submit(jpegenc.encode_jpeg, printProgress, maxFileSizeKb),
         ]
         for future in futures:
             future.result()

### 2024-01-03 Plots/create_pdfplots.py
Normalize plots

@@ -1,0 +1,40 @@
+from jinja2 import Template
+import os
+from os import path
+
+
+def create_pgfplot(filename):
+
+    template = Template(r"""
+    \documentclass{standalone}
+    \pagestyle{empty}
+    \usepackage[utf8]{inputenc}
+
+    \usepackage{tikz}
+    \usepackage{tikz-cd}
+    \usepackage{pgfplots}
+    \usepackage{layouts}
+    \pgfplotsset{compat=1.14}
+
+    \begin{document}
+    \input{{filename}}
+    \end{document}
+    """)
+
+    filename_temp = f"\u007b{filename}\u007d"
+    latex_document = template.render(filename=filename_temp)
+
+    filename = filename.replace(".pgf", ".tex")
+    
+    with open(filename, "w") as f:
+        f.write(latex_document)
+
+    # compile latex document
+    os.system(f"pdflatex {filename}")
+
+if __name__ == "__main__":
+    #get all pgf files in current folder
+    pgf_files = [file for file in os.listdir() if file.endswith(".pgf")]
+
+    for file in pgf_files:
+        create_pgfplot(file)

### 2024-01-03 scripts/evaluateMixedModel_withoutTransfer.py

@@ -42,29 +42,14 @@ def evaluate_model(model, test_loader):
     all_preds = np.array(all_preds)
     all_labels = np.array(all_labels)
     all_preds = all_preds.reshape(all_preds.shape[0], all_preds.shape[2])
-    print(all_preds.shape)
-    print(all_labels.shape)
     pca = PCA(n_components=2)
     pca.fit(all_preds)
-    print("explained variance ratio:")
-    print(pca.explained_variance_ratio_)
-    print("singular values:")
-    print(pca.singular_values_)
     all_preds = pca.transform(all_preds)
-    #print(all_preds.shape)
-    #print(all_labels.shape)
-    print(test_loader.dataset.classes)
-    #scatterplot regards to classes
-    for i in range(len(test_loader.dataset.classes)):
-        plt.scatter(all_preds[all_labels == i,0], all_preds[all_labels == i,1], label=test_loader.dataset.classes[i])
-    plt.legend()
-    plt.show()
 
-    #plt.scatter(all_preds[:,0], all_preds[:,1], c=all_labels)
-    #plt.show()
+    #set label to name from dataloader
+    all_labels = np.array([test_loader.dataset.classes[label] for label in all_labels])
 
-
-    return 
+    return all_preds, all_labels
 
 
 def main():
@@ -97,15 +82,11 @@ def main():
 
         model_name = 'resnet18'
         model = models.resnet18()
-        #num_ftrs = model.fc.in_features
-        #num_new_classes = 6
-        #model.fc = nn.Linear(num_ftrs, num_new_classes)  # Replace the final layer with the number of codec classes
-        #model.load_state_dict(torch.load('models/cnnParams_resnet18.pt'))
         print('Evaluate pretrained model ( ' + model_name + ' ) with Filesize = ' + filesize + ' kB')
         result_dictionary[filesize] = evaluate_model(model, val_loader)
 
         # store the results in a file
-        np.save('results/mixed_results.npy', result_dictionary)
+        np.save('results/wo_transfer_results.npy', result_dictionary)
 
 
 if __name__ == '__main__':

### 2024-01-03 scripts/plotResults.py

@@ -4,10 +4,16 @@ import pandas as pd
 from sklearn.metrics import confusion_matrix
 import seaborn as sn
 import pandas as pd
+import matplotlib
 
 
 RESULTS_FOLDER = 'results/'
 AVG_FILESIZE = 470
+
+#CONST for plotting so all plots are the same
+def set_figsize():
+    plt.figure(figsize=(7, 5))
+    plt.rcParams['font.size'] = 12
 
 
 def plot_accuracy_results():
@@ -17,7 +23,7 @@ def plot_accuracy_results():
     mixed_results = np.load(RESULTS_FOLDER + 'accuracy_mixed_model.npy', allow_pickle=True).item()
     keys = [int(key) for key in mixed_results.keys()]
     cmap = plt.get_cmap('tab20')
-    plt.figure(figsize=(20, 10))
+    set_figsize()
     plt.plot(keys, mixed_results.values(), color=cmap(0), label='Mixed pre trained (5-32)')
      
     mixed_self_results = np.load(RESULTS_FOLDER + 'accuracy_mixed_self_model.npy', allow_pickle=True).item()
@@ -34,7 +40,7 @@ def plot_accuracy_results():
     plt.xlabel('Test Filesize')
     plt.ylabel('Accuracy')
     plt.legend(title='Trained file sizes (mean c-rate)')
-    plt.savefig('Plots/accuracy/accuracy_comparison.png')
+    plt.savefig('Plots/accuracy/accuracy_comparison.pgf')
 
 
 def plot_confusion_matrix():
@@ -47,8 +53,8 @@ def plot_confusion_matrix():
     cmap = plt.get_cmap('tab20')
     
     for fs in filesizes:
-        plt.figure(figsize=(15,10))
-        sn.set(font_scale=1.4)
+        set_figsize()
+        #sn.set(font_scale=1.4)
         sn.heatmap(mixed_results[fs], vmin=0, vmax=100,
                xticklabels=categories, 
                yticklabels=categories, 
@@ -57,15 +63,15 @@ def plot_confusion_matrix():
                 fmt=".0f",
                annot_kws={'fontsize': 20})
         plt.xticks(rotation=45)
-        plt.savefig('Plots/conf_matrix/mixed/conf_matrix_mixed_model_fs_'+ fs + '.png')
+        plt.savefig('Plots/conf_matrix/mixed/conf_matrix_mixed_model_fs_'+ fs + '.pgf')
 
     # mixed self model
     # load dic from file
[…]

### 2024-01-03 Paper/main.tex

@@
 The dataset contains 800 train images and 100 test images.
-Since the images had different dimensions, we first had to crop them to specific in this case 512x512.
+Since the images had different dimensions, our first step was to crop all images to the same size in our case 512x512.
 Afterwards we compressed the images to specified file sizes as described in \ref{sec: filesize}.
@@
 For 10 epochs this is lower than the results we got for the transfer learning approach.
-However, if one would increase the number of epochs, we expect to reach the same levels of accuracy since the only defencemen is that the pretrained network has a preferable starting position compared to the one without transfer learning.
+However, if one would increase the number of epochs, we expect to reach the same levels of accuracy since the only difference is that the pretrained network has a preferable starting position compared to the one without transfer learning.
 This can be shown by changing the starting seed to something different leading to only 10 percent accuracy after 10 epochs.

### 2024-01-03 Plots/create_pdfplots.py
add pgf plots

@@ -30,7 +30,7 @@ def create_pgfplot(filename):
         f.write(latex_document)
 
     # compile latex document
-    os.system(f"pdflatex {filename}")
+    os.system(f"pdflatex -interaction=nonstopmode {filename} >/dev/null")
 
 if __name__ == "__main__":
     #get all pgf files in current folder

### 2024-01-03 scripts/plotResults.py

@@ -64,6 +64,7 @@ def plot_accuracy_results():
     plt.ylabel('Accuracy')
     plt.legend(title='Trained file sizes (mean c-rate)')
     plt.savefig('Plots/accuracy/accuracy_comparison.pgf')
+    plt.close()
 
     filesizes = ['10', '25', '40', '100']
 
@@ -89,7 +90,7 @@ def plot_accuracy_results():
     plt.ylabel('Accuracy')
     plt.legend(title='Trained file sizes (mean c-rate)')
     plt.savefig('Plots/accuracy/accuracy_comparison_filtered.pgf')
-
+    plt.close()
 
 
 def plot_confusion_matrix():
@@ -107,10 +108,10 @@ def plot_confusion_matrix():
                    yticklabels=categories,
                    annot=True,
                    cmap='Blues',
-                   fmt=".0f",
-                   annot_kws={'fontsize': 20})
+                   fmt=".0f")
         plt.xticks(rotation=45)
         plt.savefig('Plots/conf_matrix/mixed/conf_matrix_mixed_model_fs_' + fs + '.pgf')
+        plt.close()
 
     # mixed self model
     # load dic from file
@@ -124,11 +125,11 @@ def plot_confusion_matrix():
                    yticklabels=categories,
                    annot=True,
                    cmap='Blues',
-                   fmt=".0f",
-                   annot_kws={'fontsize': 20})
+                   fmt=".0f")
         plt.xticks(rotation=45)
         plt.tight_layout()
         plt.savefig('Plots/conf_matrix/mixed_self/conf_matrix_mixed_self_model_fs_' + fs + '.pgf')
+        plt.close()
 
     # filesize model
     for fs in filesizes:
@@ -144,11 +145,11 @@ def plot_confusion_matrix():
                        yticklabels=categories,
                        annot=True,
                        cmap='Blues',
-                       fmt=".0f",
-                       annot_kws={'fontsize': 20})
+                       fmt=".0f",)
             plt.xticks(rotation=45)
             plt.tight_layout()
             plt.savefig('Plots/conf_matrix/' + fs + '/conf_matrix_fs_'+ ev_size + '.pgf')
+            plt.close()
 
 def plot_confusion_matrix_all():
     filesizes = ['5', '10', '17', '25', '32', '40', '50', '60', '75', '100']
[…]

### 2024-01-07 scripts/avifenc.py
Add time measure to quality evaluation (#85)
* Add time measure to quality evaluation

* change plots to pgf

* add pgf plots and np results file for quality

* remove comments

---------

Co-authored-by: Stefan Findenig <s.findenig@gmail.com>
Co-authored-by: Moritz Langer <moritz.langer@redbull.com>
Co-authored-by: Moritz Langer <85168282+m-langer@users.noreply.github.com>

@@ -1,4 +1,6 @@
 # %pip install pillow-avif-plugin
+from datetime import datetime
+
 import pillow_avif
 from PIL import Image
 import os
@@ -107,11 +109,13 @@ def encode_avif_q(image_path, decoded_path, q):
     image = Image.open(image_path)
     # save image with new quality
     outputPath = 'temp' + outputFileExtension
+    start_time = datetime.now()
     image.save(outputPath, quality=int(q))
+    compression_time = (datetime.now() - start_time).microseconds / 1000
     enc_size = os.path.getsize(outputPath)
     decode_avif(outputPath, decoded_path, False)
     os.system('rm ' + outputPath)
-    return enc_size
+    return enc_size, compression_time
 
 
 if __name__ == '__main__':

### 2024-01-07 scripts/bpgenc.py

@@ -1,5 +1,7 @@
 import os
 import glob
+from datetime import datetime
+
 import numpy as np
 from filesizelogger import log_filesize
 
@@ -102,11 +104,13 @@ def encode_bpg_q(image_path, decoded_path, q):
     normalized_q = int(maxQ * (q / 100))
     # save image with new quality
     outputPath = 'temp' + outputFileExtension
+    start_time = datetime.now()
     os.system('bpgenc -o ' + outputPath + ' -q ' + str(int(maxQ - normalized_q)) + ' ' + image_path)
+    compression_time = (datetime.now() - start_time).microseconds / 1000
     enc_size = os.path.getsize(outputPath)
     decode_bpg(outputPath, decoded_path, False)
     os.system('rm ' + outputPath)
-    return enc_size
+    return enc_size, compression_time
 
 
 if __name__ == '__main__':

### 2024-01-07 scripts/evaluateMixedModel_withoutTransfer.py

@@ -20,8 +20,7 @@ def evaluate_model(model, test_loader):
 
     model.to(device)
     model.eval()
-    correct = 0
-    total = 0
+
     all_preds = []
     all_labels = []
 
@@ -32,8 +31,6 @@ def evaluate_model(model, test_loader):
             outputs = model(images)
             #l2 norm
             outputs = nn.functional.normalize(outputs, p=2, dim=1)
-            
-            total += labels.size(0)  # Update the total count of processed samples
 
             all_preds.append(outputs.cpu().numpy())
             all_labels.extend(labels.cpu().numpy())
@@ -46,25 +43,19 @@ def evaluate_model(model, test_loader):
     print(all_labels.shape)
     pca = PCA(n_components=2)
     pca.fit(all_preds)
+
     print("explained variance ratio:")
     print(pca.explained_variance_ratio_)
     print("singular values:")
     print(pca.singular_values_)
+
     all_preds = pca.transform(all_preds)
-    #print(all_preds.shape)
-    #print(all_labels.shape)
-    print(test_loader.dataset.classes)
     #scatterplot regards to classes
     for i in range(len(test_loader.dataset.classes)):
         plt.scatter(all_preds[all_labels == i,0], all_preds[all_labels == i,1], label=test_loader.dataset.classes[i])
     plt.legend()
+    plt.savefig('Plots/loss_comparison/Without_Transferlearning_model.pgf')
     plt.show()
-
-    #plt.scatter(all_preds[:,0], all_preds[:,1], c=all_labels)
-    #plt.show()
-
-
-    return 
 
 
 def main():
@@ -97,10 +88,7 @@ def main():
 
         model_name = 'resnet18'
         model = models.resnet18()
-        #num_ftrs = model.fc.in_features
-        #num_new_classes = 6
-        #model.fc = nn.Linear(num_ftrs, num_new_classes)  # Replace the final layer with the number of codec classes
-        #model.load_state_dict(torch.load('models/cnnParams_resnet18.pt'))
+        
         print('Evaluate pretrained model ( ' + model_name + ' ) with Filesize = ' + filesize + ' kB')
         result_dictionary[filesize] = evaluate_model(model, val_loader)
 

### 2024-01-07 scripts/jpeg2000enc.py

@@ -1,6 +1,8 @@
 import subprocess
 import os
 import glob
+from datetime import datetime
+
 import numpy as np
 from filesizelogger import log_filesize
 
@@ -115,14 +117,16 @@ def encode_jpeg2k(printProgress=False, maxFileSizeKb=32, useMultiCropPerImage=Fa
 def encode_jpeg2k_q(image_path, decoded_path, q):
     # save image with new quality
     outputPath = 'temp' + outputFileExtension
+    start_time = datetime.now()
     subprocess.call('opj_compress -o ' + outputPath + ' -r ' + str(q) + ' -i ' + image_path,
                     stdout=subprocess.DEVNULL,
                     stderr=subprocess.DEVNULL,
                     shell=True)
+    compression_time = (datetime.now() - start_time).microseconds / 1000
     enc_size = os.path.getsize(outputPath)
     decode_jpeg2k(outputPath, decoded_path, False)
     os.system('rm ' + outputPath)
-    return enc_size
+    return enc_size, compression_time
 
 
 if __name__ == '__main__':

### 2024-01-07 scripts/jpegenc.py

@@ -1,3 +1,5 @@
+from datetime import datetime
+
 from PIL import Image
 import os
 import glob
@@ -102,11 +104,13 @@ def encode_jpeg_q(image_path, decoded_path, q):
     image = Image.open(image_path)
     # save image with new quality
     outputPath = 'temp' + outputFileExtension
+    start_time = datetime.now()
     image.save(outputPath, quality=int(q))
+    compression_time = (datetime.now() - start_time).microseconds / 1000
     enc_size = os.path.getsize(outputPath)
     decode_jpeg(outputPath, decoded_path, False)
     os.system('rm ' + outputPath)
-    return enc_size
+    return enc_size, compression_time
 
 
 if __name__ == '__main__':

### 2024-01-07 scripts/jpegxl.py

@@ -1,6 +1,8 @@
 import os
 import subprocess
 import glob
+from datetime import datetime
+
 import numpy as np
 from imagecodecs import imread, imwrite
 from filesizelogger import log_filesize
@@ -105,11 +107,13 @@ def encode_jpgxl(printProgress=False, maxFileSizeKb=32, useMultiCropPerImage=Fal
 def encode_jxl_q(image_path, decoded_path, q):
     # save image with new quality
     outputPath = 'temp' + outputFileExtension
+    start_time = datetime.now()
     subprocess.call(['cjxl', image_path, outputPath, '--quiet', '-q', str(q)])
+    compression_time = (datetime.now() - start_time).microseconds / 1000
     enc_size = os.path.getsize(outputPath)
     decode_jpgxl(outputPath, decoded_path, False)
     os.system('rm ' + outputPath)
-    return enc_size
+    return enc_size, compression_time
 
 
 if __name__ == '__main__':

### 2024-01-07 scripts/jxrenc_0.py

@@ -1,7 +1,10 @@
 import os
 import glob
+from datetime import datetime
+
 import numpy as np
 from PIL import Image
+from filesizelogger import log_filesize
 
 minQ = 1
 # to increase the floating point precision this high value is needed (q needs to be in range 0-1)
@@ -118,6 +121,7 @@ def encode_jxr(printProgress=False, maxFileSizeKb=32, useMultiCropPerImage=False
                 f_size = os.path.getsize(outputPath) / 1024
                 i += 1
                 print('Image: ' + file_name + ' Quality: ' + str(q) + ' Filesize: ' + str(f_size) + ' kb' + ' Progress: ' + str(i) + '/' + str(number_of_files))
+                log_filesize(f_size, maxFileSizeKb, usedCodec)
 
             dec_file_name = file_name.split(sep='.')[0] + '_' + str(maxFileSizeKb) + tifFileExtension
             dec_path = pathImagesEncoded[:-len(usedCodec)] + decodedFolder + str(maxFileSizeKb)+ "/" + usedCodec + dec_file_name
@@ -129,11 +133,13 @@ def encode_jxr_q(image_path, decoded_path, q):
     im = Image.open(image_path)
     im.save(tif_path, quality=100)
     q_string = str(q) if q <= 1 else str(int(q))
+    start_time = datetime.now()
     os.system('JxrEncApp -q ' + q_string + ' -o ' + outputPath + ' -i ' + tif_path + ' ' + overlapParameter)
+    compression_time = (datetime.now() - start_time).microseconds / 1000
     enc_size = os.path.getsize(outputPath)
     decode_jxr(outputPath, tif_path, False)
     os.system('rm temp*')
-    return enc_size
+    return enc_size, compression_time
 
 
 if __name__ == '__main__':

### 2024-01-07 scripts/jxrenc_1.py

@@ -1,5 +1,7 @@
 import os
 import glob
+from datetime import datetime
+
 import numpy as np
 from PIL import Image
 from filesizelogger import log_filesize
@@ -128,11 +130,13 @@ def encode_jxr_q(image_path, decoded_path, q):
     im = Image.open(image_path)
     im.save(tif_path, quality=100)
     q_string = str(q) if q <= 1 else str(int(q))
+    start_time = datetime.now()
     os.system('JxrEncApp -q ' + q_string + ' -o ' + outputPath + ' -i ' + tif_path + ' ' + overlapParameter)
+    compression_time = (datetime.now() - start_time).microseconds / 1000
     enc_size = os.path.getsize(outputPath)
     decode_jxr(outputPath, tif_path, False)
     os.system('rm temp*')
-    return enc_size
+    return enc_size, compression_time
 
 
 if __name__ == '__main__':

### 2024-01-07 scripts/jxrenc_2.py

@@ -1,7 +1,10 @@
 import os
 import glob
+from datetime import datetime
+
 import numpy as np
 from PIL import Image
+from filesizelogger import log_filesize
 
 minQ = 1
 # to increase the floating point precision this high value is needed (q needs to be in range 0-1)
@@ -114,6 +117,7 @@ def encode_jxr(printProgress=False, maxFileSizeKb=32, useMultiCropPerImage=False
                 f_size = os.path.getsize(outputPath) / 1024
                 i += 1
                 print('Image: ' + file_name + ' Quality: ' + str(q) + ' Filesize: ' + str(f_size) + ' kb' + ' Progress: ' + str(i) + '/' + str(number_of_files))
+                log_filesize(f_size, maxFileSizeKb, usedCodec)
 
             dec_file_name = file_name.split(sep='.')[0] + '_' + str(maxFileSizeKb) + tifFileExtension
             dec_path = pathImagesEncoded[:-len(usedCodec)] + decodedFolder + str(maxFileSizeKb)+ "/" + usedCodec + dec_file_name
@@ -125,11 +129,13 @@ def encode_jxr_q(image_path, decoded_path, q):
     im = Image.open(image_path)
     im.save(tif_path, quality=100)
     q_string = str(q) if q <= 1 else str(int(q))
+    start_time = datetime.now()
     os.system('JxrEncApp -q ' + q_string + ' -o ' + outputPath + ' -i ' + tif_path + ' ' + overlapParameter)
+    compression_time = (datetime.now() - start_time).microseconds / 1000
     enc_size = os.path.getsize(outputPath)
     decode_jxr(outputPath, tif_path, False)
     os.system('rm temp*')
-    return enc_size
+    return enc_size, compression_time
 
 
 if __name__ == '__main__':

### 2024-01-07 scripts/plotResults.py

@@ -1,4 +1,13 @@
 import matplotlib.pyplot as plt
+import matplotlib
+#Make matplotlib use latex for font rendering
+matplotlib.use("pgf")
+matplotlib.rcParams.update({
+    "pgf.texsystem": "pdflatex",
+    'font.family': 'serif',
+    'text.usetex': True,
+    'pgf.rcfonts': False,
+})
 import numpy as np
 import pandas as pd
 from sklearn.metrics import confusion_matrix
@@ -34,7 +43,7 @@ def plot_accuracy_results():
     plt.xlabel('Test Filesize')
     plt.ylabel('Accuracy')
     plt.legend(title='Trained file sizes (mean c-rate)')
-    plt.savefig('Plots/accuracy/accuracy_comparison.png')
+    plt.savefig('Plots/accuracy/accuracy_comparison.pgf')
 
 
 def plot_confusion_matrix():
@@ -57,7 +66,7 @@ def plot_confusion_matrix():
                 fmt=".0f",
                annot_kws={'fontsize': 20})
         plt.xticks(rotation=45)
-        plt.savefig('Plots/conf_matrix/mixed/conf_matrix_mixed_model_fs_'+ fs + '.png')
+        plt.savefig('Plots/conf_matrix/mixed/conf_matrix_mixed_model_fs_'+ fs + '.pgf')
 
     # mixed self model
     # load dic from file
@@ -75,7 +84,7 @@ def plot_confusion_matrix():
                annot_kws={'fontsize': 20})
         plt.xticks(rotation=45)
         plt.tight_layout()
-        plt.savefig('Plots/conf_matrix/mixed_self/conf_matrix_mixed_self_model_fs_'+ fs + '.png')
+        plt.savefig('Plots/conf_matrix/mixed_self/conf_matrix_mixed_self_model_fs_'+ fs + '.pgf')
 
     # filesize model
     for fs in filesizes:
@@ -95,7 +104,7 @@ def plot_confusion_matrix():
                 annot_kws={'fontsize': 20})
             plt.xticks(rotation=45)
             plt.tight_layout()
-            plt.savefig('Plots/conf_matrix/' + fs + '/conf_matrix_fs_'+ ev_size + '.png')
+            plt.savefig('Plots/conf_matrix/' + fs + '/conf_matrix_fs_'+ ev_size + '.pgf')
 
 def plot_confusion_matrix_all():
[…]

### 2024-01-07 scripts/preprocessing.py

@@ -44,8 +44,8 @@ async def preprocess(cropNeeded=False,
 
 
 if __name__ == '__main__':
-    #filesizes = [5, 10, 17, 25, 32, 40, 50, 60, 75, 100]
-    filesizes = [10]
+    filesizes = [5, 10, 17, 25, 32, 40, 50, 60, 75, 100]
+    #filesizes = [5]
     for filesize in filesizes:
         asyncio.run(preprocess(maxFileSizeKb=filesize))
    

### 2024-01-07 scripts/quality.py

@@ -6,11 +6,22 @@ import os
 # affected devices: macOS on Apple Silicon
 # https://github.com/bigcat88/pillow_heif/issues/89
 import pillow_heif
+
 pillow_heif.register_heif_opener()
 ### END DISCLAIMER ###
 
 import cv2
 import matplotlib.pyplot as plt
+import matplotlib
+#Make matplotlib use latex for font rendering
+matplotlib.use("pgf")
+matplotlib.rcParams.update({
+    "pgf.texsystem": "pdflatex",
+    'font.family': 'serif',
+    'text.usetex': True,
+    'pgf.rcfonts': False,
+})
+
 import numpy as np
 from PIL import Image
 
@@ -41,6 +52,7 @@ def calc_psnr(original_image_path, decoded_image_path):
         return float('inf')
     return 20 * np.log10(np.array(orig).max() / np.sqrt(mse))
 
+
 def calc_ssim(orig_image_path, dec_image_path):
     orig_image = cv2.imread(orig_image_path)
     dec_image = cv2.imread(dec_image_path)
@@ -52,7 +64,7 @@ def calc_ssim(orig_image_path, dec_image_path):
     # Constants to stabilize the division with weak denominator
     k1 = 0.01
     k2 = 0.03
-    L = 2**8 - 1  # 8-bit dynamic range of pixel-values
+    L = 2 ** 8 - 1  # 8-bit dynamic range of pixel-values
     C1 = (k1 * L) ** 2
     C2 = (k2 * L) ** 2
 
@@ -68,33 +80,32 @@ def calc_ssim(orig_image_path, dec_image_path):
     mu2 = cv2.GaussianBlur(I2, **opts)
 
     # Variance
-    sigma1_2 = cv2.GaussianBlur(I1**2, **opts) - mu1**2
-    sigma2_2 = cv2.GaussianBlur(I2**2, **opts) - mu2**2
+    sigma1_2 = cv2.GaussianBlur(I1 ** 2, **opts) - mu1 ** 2
+    sigma2_2 = cv2.GaussianBlur(I2 ** 2, **opts) - mu2 ** 2
 
     # Covariance
     sigma12 = cv2.GaussianBlur(I1 * I2, **opts) - mu1 * mu2
 
     # SSIM index
     num = (2 * mu1 * mu2 + C1) * (2 * sigma12 + C2)
[…]

### 2024-01-07 Paper/main.tex
Add description of codecs (#88)

@@
 \subsection{AVIF, JPEG and WebP}
+\subsubsection{AVIF}
+AVIF is a format that utilizes the AV1 video codec.
+The AV1 codec employs block-based predictive coding.
+In this method, the frame is broken down into smaller units.
+Those are then analyzed to predict repetitive motion and color data based on blocks that have been processed earlier.
+Once the prediction is made, the redundant data is removed from the block.
+To convert the image into a sum of cosine functions of different frequencies the Discrete Cosine Transform (DCT) is used.
+
+\subsubsection{JPEG}
+JPEG uses the Discrete Cosine Transform (DCT) to convert an image into a sum of cosine functions of different frequencies.
+After the DCT, the coefficients are quantized to reduce their precision, and then entropy coded to compress the resulting data.
+The entropy coding method used in JPEG is Huffman coding.
+
+\subsubsection{WebP}
+In WebP a similar compression mechanism to that of the VP8 codec is used.
+This involves segmenting the frame into smaller units.
+Each of those units motion and color information is predicted based on previously processed blocks.
+This prediction process allows for the removal of redundant data from each block.
+The remaining data is then transformed using the Discrete Cosine Transform (DCT).
+
 For those encoders the python package pillow-avif-plugin and pillow was used.
@@
 \subsection{BPG}
+The Better Portable Graphics (BPG) codec is a digital image coding file format, developed by Fabrice Bellard.
+It’s built upon the intra-frame encoding of the High Efficiency Video Coding (HEVC) video compression standard.
+
+BPG operates on a block-by-block basis to transform image data into a form that minimizes redundancy.
+It employs high-quality decimation and interpolation (using 10 tap Lanczos filter and 7 tap Lanczos filter respectively) to manage chroma samples in 4:2:2 and 4:2:0 formats.
+
 To encode the images in BPG the Linux distribution from Fabrice Bellard's website (https://bellard.org/bpg/) was used.
@@
 \subsection{HEIC}
+The High Efficiency Image File (HEIF) container, which uses the High Efficiency Video Coding (HEVC) compression standard, is the basis for the HEIC codec.
+This codec is used for storing both images and videos.
+The transformation is applied to pixel blocks, the size of which can range from 4x4 to 32x32.
+Depending on the type of block and the prediction mode, the transformation can be either a discrete cosine transform (DCT) or a discrete sine transform (DST).
+Depending on the profile and level of the HEVC standard, the entropy coding can be either a context-adaptive binary arithmetic coding (CABAC) or a context-adaptive variable-length coding (CAVLC).
+
 Same as with the AVIF codec HEIC is also supported in a python package.
@@
 \subsection{JPEG2000}
+In JPEG2000, the transformation process employs a discrete wavelet transform (DWT).
+The original image is divided into rectangular tiles that do not overlap.
+These tiles are then broken down into different levels of decomposition using DWT.
+Each level of decomposition contains a number of subbands, which are made up of coefficients that represent the characteristics of the original tile component’s horizontal and vertical spatial frequencies.
+For entropy coding JPEG2000 uses Embedded Block Coding with Optimized Truncation (EBCOT).
+EBCOT is a context-based binary arithmetic encoder that consists of a Context Extractor (CE) and an Arithmetic Coder (AC).
+
 For the JPEG standards JPEG itself provides software to encode images.
@@
 \subsection{JXL}
+JXL also uses the same basic technologies as JPEG2000, but with some improvements and innovations, such as learned lifting-based DWT and learned tree-based entropy coding.
+
 For JPEG XL the JPEG organization also provides a package which can be installed in Linux.
@@
 \subsection{JXR}
+JXR uses a unique method that breaks down an image into smaller, individual rectangular tile areas.
+This is different from JPEG, which uses a single transformation stage.
+Instead, JXR applies its 4x4 core transform in a two-level hierarchical manner within 16x16 macroblock regions.
+This approach gives the transform a wavelet-like multi-resolution hierarchy, which enhances its compression capability.
+
+When it comes to entropy coding, JXR’s process is more adaptable and intricate than JPEG’s.
+It includes a DC and AC coefficient prediction scheme, adaptive coefficient reordering (as opposed to JPEG’s fixed zigzag ordering), and a type of adaptive Huffman coding for the coefficients themselves.
+This entropy coding process enables efficient representation of the image data, which contributes to the overall compression performance.
+
+Additionaly the Photo Overlap Transform (POT) is a key operation in JPEG XR encoding that reduces blocking artefacts and improves compression efficiency.
+There are three ways of setting the POT in JPEG XR, depending on the image format and the compression mode:
+
+\textbf{No POT:} This is the simplest option, where no POT is applied to the image blocks. This is suitable for lossless compression or images with low bit depth (8 bits or less per channel).
+
+\textbf{Half POT:} This option applies POT to half of the image blocks, alternating between odd and even rows and columns.
+This reduces the computation complexity and memory requirement of the POT, while still providing some benefits of overlap processing.
+This is suitable for lossy compression or images with medium bit depth (9 to 15 bits per channel).
+
+\textbf{Full POT:} This option applies POT to all of the image blocks, creating a full overlap between adjacent blocks.
+This maximizes the quality and compression performance of the POT, but also increases the computation complexity and memory requirement.
+This is suitable for high-quality compression or images with high bit depth (16 bits or more per channel).
+
 For JXR the package libjxr-devtools was used.

### 2024-01-07 Plots/create_pdfplots.py
Feature/unify plots (#87)
* Add time measure to quality evaluation

* change plots to pgf

* add pgf plots and np results file for quality

* remove comments

* change accuracy plot and save fig as .pgf

* add pgf plorts from plot resutls py

* add pgf plots with pngs and npy results

* Normalize plots

* add pgf plots

* Change images to pgfs in Paper

---------

Co-authored-by: Michael Hafner <hafneer@gmail.com>
Co-authored-by: Stefan Findenig <s.findenig@gmail.com>
Co-authored-by: aleksandarRa <radovic.aleksandar@gmx.at>

@@ -1,0 +1,40 @@
+from jinja2 import Template
+import os
+from os import path
+
+
+def create_pgfplot(filename):
+
+    template = Template(r"""
+    \documentclass{standalone}
+    \pagestyle{empty}
+    \usepackage[utf8]{inputenc}
+
+    \usepackage{tikz}
+    \usepackage{tikz-cd}
+    \usepackage{pgfplots}
+    \usepackage{layouts}
+    \pgfplotsset{compat=1.14}
+
+    \begin{document}
+    \input{{filename}}
+    \end{document}
+    """)
+
+    filename_temp = f"\u007b{filename}\u007d"
+    latex_document = template.render(filename=filename_temp)
+
+    filename = filename.replace(".pgf", ".tex")
+    
+    with open(filename, "w") as f:
+        f.write(latex_document)
+
+    # compile latex document
+    os.system(f"pdflatex -interaction=nonstopmode {filename} >/dev/null")
+
+if __name__ == "__main__":
+    #get all pgf files in current folder
+    pgf_files = [file for file in os.listdir() if file.endswith(".pgf")]
+
+    for file in pgf_files:
+        create_pgfplot(file)

### 2024-01-07 scripts/cnnDataset.py

@@ -7,10 +7,10 @@ from torchvision import transforms
 # create a training and test dataset
 def create_dataset(transform=transforms.ToTensor(), filesize="all"):
     # create a training dataset from multiple image folders 'Images/DIV2K_train_HR'
-    trainset = torchvision.datasets.ImageFolder(root='Images/DIV2K_train_HR/Decoded_pieces/'+filesize+'/', transform=transform)
+    trainset = torchvision.datasets.ImageFolder(root='Images/DIV2K_train_HR/Decoded/'+filesize+'/', transform=transform)
     # target_transform = Lambda(lambda y: torch.zeros(10, dtype=torch.float).scatter_(dim=0, index=torch.tensor(y), value=1))
     # create a test dataset from multiple image folders 'Images/DIV2K_valid_HR'
-    testset = torchvision.datasets.ImageFolder(root='Images/DIV2K_valid_HR/Decoded_pieces/'+filesize+'/', transform=transform)
-    trainloader = torch.utils.data.DataLoader(trainset, batch_size=16, shuffle=True)
-    testloader = torch.utils.data.DataLoader(testset, batch_size=16, shuffle=False)
+    testset = torchvision.datasets.ImageFolder(root='Images/DIV2K_valid_HR/Decoded/'+filesize+'/', transform=transform)
+    trainloader = torch.utils.data.DataLoader(trainset, batch_size=1, shuffle=True)
+    testloader = torch.utils.data.DataLoader(testset, batch_size=1, shuffle=False)
     return trainloader, testloader

### 2024-01-07 scripts/evaluateMixedModel_withoutTransfer.py

@@ -39,23 +39,14 @@ def evaluate_model(model, test_loader):
     all_preds = np.array(all_preds)
     all_labels = np.array(all_labels)
     all_preds = all_preds.reshape(all_preds.shape[0], all_preds.shape[2])
-    print(all_preds.shape)
-    print(all_labels.shape)
     pca = PCA(n_components=2)
     pca.fit(all_preds)
-
-    print("explained variance ratio:")
-    print(pca.explained_variance_ratio_)
-    print("singular values:")
-    print(pca.singular_values_)
-
     all_preds = pca.transform(all_preds)
-    #scatterplot regards to classes
-    for i in range(len(test_loader.dataset.classes)):
-        plt.scatter(all_preds[all_labels == i,0], all_preds[all_labels == i,1], label=test_loader.dataset.classes[i])
-    plt.legend()
-    plt.savefig('Plots/loss_comparison/Without_Transferlearning_model.pgf')
-    plt.show()
+
+    #set label to name from dataloader
+    all_labels = np.array([test_loader.dataset.classes[label] for label in all_labels])
+
+    return all_preds, all_labels
 
 
 def main():
@@ -88,12 +79,12 @@ def main():
 
         model_name = 'resnet18'
         model = models.resnet18()
-        
+
         print('Evaluate pretrained model ( ' + model_name + ' ) with Filesize = ' + filesize + ' kB')
         result_dictionary[filesize] = evaluate_model(model, val_loader)
 
         # store the results in a file
-        np.save('results/mixed_results.npy', result_dictionary)
+        np.save('results/wo_transfer_results.npy', result_dictionary)
 
 
 if __name__ == '__main__':

### 2024-01-07 scripts/plotResults.py

@@ -9,14 +9,17 @@ matplotlib.rcParams.update({
     'pgf.rcfonts': False,
 })
 import numpy as np
-import pandas as pd
-from sklearn.metrics import confusion_matrix
 import seaborn as sn
 import pandas as pd
-
+import matplotlib
 
 RESULTS_FOLDER = 'results/'
 AVG_FILESIZE = 470
+
+#CONST for plotting so all plots are the same
+def set_figsize():
+    plt.figure(figsize=(7, 5))
+    plt.rcParams['font.size'] = 12
 
 
 def plot_accuracy_results():
@@ -25,25 +28,69 @@ def plot_accuracy_results():
     # load dic from file
     mixed_results = np.load(RESULTS_FOLDER + 'accuracy_mixed_model.npy', allow_pickle=True).item()
     keys = [int(key) for key in mixed_results.keys()]
+
+    # Map file sizes to colors
+    color_dict = {
+        'pre': plt.get_cmap('Paired')(1),
+        'self': plt.get_cmap('Paired')(3),
+        '5':  plt.get_cmap('Paired')(5),
+        '10': plt.get_cmap('Paired')(7),
+        '17': plt.get_cmap('Paired')(9),
+        '25': plt.get_cmap('Dark2')(6),
+        '32': plt.get_cmap('Accent')(5),
+        '40': plt.get_cmap('Accent')(7),
+        '50': plt.get_cmap('Set2')(4),
+        '60': plt.get_cmap('tab10')(9),
+        '75': plt.get_cmap('tab20b')(19),
+        '100': plt.get_cmap('Pastel1')(0)
+    }
+
     cmap = plt.get_cmap('tab20')
-    plt.figure(figsize=(20, 10))
+    set_figsize()
     plt.plot(keys, mixed_results.values(), color=cmap(0), label='Mixed pre trained (5-32)')
      
     mixed_self_results = np.load(RESULTS_FOLDER + 'accuracy_mixed_self_model.npy', allow_pickle=True).item()
     keys = [int(key) for key in mixed_self_results.keys()]
-    plt.plot(keys, mixed_self_results.values(), color=cmap(15), label='Mixed self trained (5-32)')
+    plt.plot(keys, mixed_self_results.values(), color=color_dict['self'], label='Mixed self trained (5-32)')
 
-    for i, filesize in enumerate(filesizes):
+    for filesize in filesizes:
[…]

### 2024-01-12 scripts/plotResults.py
add accuracy plot without mixed models

@@ -66,6 +66,21 @@ def plot_accuracy_results():
     plt.savefig('Plots/accuracy/accuracy_comparison.pgf')
     plt.close()
 
+    # plot accuracy without mixed models
+    for filesize in filesizes:
+        res_dict = np.load(RESULTS_FOLDER + 'accuracy_fs_' + filesize + '_model.npy', allow_pickle=True).item()
+        keys = [int(key) for key in res_dict.keys()]
+        plt.plot(keys, res_dict.values(), color=color_dict[filesize],
+                 label=filesize + f'  c-rate: {(AVG_FILESIZE / float(filesize)):.2f}')
+
+    plt.grid()
+    plt.xlabel('Test Filesize')
+    plt.ylabel('Accuracy')
+    plt.legend(title='Trained file sizes (mean c-rate)')
+    plt.savefig('Plots/accuracy/accuracy_comparison_withoutMixed.pgf')
+    plt.close()
+
+    # plot filtered accuracy
     filesizes = ['10', '25', '40', '100']
 
     # load dic from file

### 2024-01-13 scripts/plotResults.py
fix JXR 1 compressing to 10 kb & add JXR2

@@ -290,10 +290,10 @@ def plot_filesize_to_target():
     plt.axhline(y=32, color='green', linestyle='--', label='Target')
     # legend
     plt.legend(title='Codec')
-    plt.title('Actual Filesize to Target Comparison')
     plt.grid()
     plt.xlabel('Codec')
     plt.ylabel('Filesize (KB)')
+    plt.xticks(rotation=45)
     plt.savefig('Plots/filesize_to_target.pgf')
     plt.close()
 
@@ -331,13 +331,13 @@ def main():
     'pgf.rcfonts': False,
     })
 
-    plot_accuracy_results()
-    plot_loss_results() 
+    #plot_accuracy_results()
+    #plot_loss_results() 
     plot_filesize_to_target()
-    plot_confusion_matrix()
-    plot_confusion_matrix_all()
-    plot_dec_enc_time()
-    plot_scatter_without_transfer()
+    #plot_confusion_matrix()
+    #plot_confusion_matrix_all()
+    #plot_dec_enc_time()
+    #plot_scatter_without_transfer()
 
 
 if __name__ == '__main__':

### 2024-01-13 scripts/plotResults.py
include all plots again

@@ -331,13 +331,13 @@ def main():
     'pgf.rcfonts': False,
     })
 
-    #plot_accuracy_results()
-    #plot_loss_results() 
+    plot_accuracy_results()
+    plot_loss_results() 
     plot_filesize_to_target()
-    #plot_confusion_matrix()
-    #plot_confusion_matrix_all()
-    #plot_dec_enc_time()
-    #plot_scatter_without_transfer()
+    plot_confusion_matrix()
+    plot_confusion_matrix_all()
+    plot_dec_enc_time()
+    plot_scatter_without_transfer()
 
 
 if __name__ == '__main__':

### 2024-01-14 Paper/main.tex
Change images to pgfs in Paper
Feature/unify plots (#87)
* Add time measure to quality evaluation

* change plots to pgf

* add pgf plots and np results file for quality

* remove comments

* change accuracy plot and save fig as .pgf

* add pgf plorts from plot resutls py

* add pgf plots with pngs and npy results

* Normalize plots

* add pgf plots

* Change images to pgfs in Paper

---------

Co-authored-by: Michael Hafner <hafneer@gmail.com>
Co-authored-by: Stefan Findenig <s.findenig@gmail.com>
Co-authored-by: aleksandarRa <radovic.aleksandar@gmx.at>
Add description for no transfer learnin

@@
 	\centering
-	\includegraphics[width=12cm]{filesize_comparison.png}
+	\resizebox{\textwidth}{!}{\input{../Plots/filesize_to_target.pgf}}
 	\caption{Archived filesizes for used encoder}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{psnr.png}
+        \resizebox{\textwidth}{!}{\input{../Plots/psnr.pgf}}
           \caption{PSNR comparison of the used codecs}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../Plots/ssim.png}
+        \resizebox{\textwidth}{!}{\input{../Plots/ssim.pgf}}
           \caption{SSIM comparison of the used codecs}
@@
 
+\subsection{Evaluation of ResNet Performance Without Transfer Learning} 
+Prior to the implementation of transfer learning methodologies, an analysis was conducted to ascertain whether the selected ResNet architecture could independently identify various image compression algorithms.
+The entire dataset of one specific compression size, was processed through the model, and the outputs were L2 normalized.
+This resulted in 1000 dimension vectors for each image.
+
+To make sense of these results, we used Principal Component Analysis (PCA) on all the vectors and plotted them on a scatter plot as it can be seen in Figure \ref{fig: no_transfer}.
+The scatter plot reveals that for images compressed to 10kB, there is no discernible clustering pattern specific to a single compression algorithm.
+However, it is observed that certain clusters exist where multiple compression algorithms are in close proximity to each other.
+This observation aligns with the inherent capability of the original network to classify images.
+Consequently, the images utilized across different compression algorithms form these compact clusters.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{Plots/plot_scatter_without_transfer_10.pgf}
+	\caption{10kB Compression: ResNet without transfer learning}
+	\label{fig: no_transfer}
+\end{figure}
+
 \section{Performance}
@@
 	\centering
-	\includegraphics[width=12cm]{accuracy_comparison.png}
+	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison.pgf}}
 	\caption{Accuracy Comparison}
@@
         \centering
-        \includegraphics[width=1\linewidth]{loss_comparison_filesize_10.png}
+        \resizebox{\textwidth}{!}{\input{../Plots/loss_comparison/loss_comparison_fs_10_model.pgf}}
         \caption{Loss of model with filesize 10}
@@
         \centering
-        \includegraphics[width=1\linewidth]{loss_comparison_mixed.png}
+        \resizebox{\textwidth}{!}{\input{../Plots/loss_comparison/loss_comparison_fs_mixed_model.pgf}}
         \caption{Loss of mixed model}

### 2024-01-14 scripts/plotResults.py
Adapt legend alignment

@@ -62,11 +62,15 @@ def plot_accuracy_results():
     plt.grid()
     plt.xlabel('Test Filesize')
     plt.ylabel('Accuracy')
-    plt.legend(title='Trained file sizes (mean c-rate)')
+    plt.legend(title='Trained file sizes (mean c-rate)', loc='upper left', bbox_to_anchor=(1, 1))
+    plt.gcf().set_size_inches(9, 5)
+    # Use tight_layout to ensure all elements fit within the saved area
+    plt.tight_layout()
     plt.savefig('Plots/accuracy/accuracy_comparison.pgf')
     plt.close()
 
     # plot accuracy without mixed models
+    set_figsize()
     for filesize in filesizes:
         res_dict = np.load(RESULTS_FOLDER + 'accuracy_fs_' + filesize + '_model.npy', allow_pickle=True).item()
         keys = [int(key) for key in res_dict.keys()]
@@ -76,7 +80,10 @@ def plot_accuracy_results():
     plt.grid()
     plt.xlabel('Test Filesize')
     plt.ylabel('Accuracy')
-    plt.legend(title='Trained file sizes (mean c-rate)')
+    plt.legend(title='Trained file sizes (mean c-rate)', loc='upper left', bbox_to_anchor=(1, 1))
+    plt.gcf().set_size_inches(9, 5)
+    # Use tight_layout to ensure all elements fit within the saved area
+    plt.tight_layout()
     plt.savefig('Plots/accuracy/accuracy_comparison_withoutMixed.pgf')
     plt.close()
 
@@ -103,7 +110,10 @@ def plot_accuracy_results():
     plt.grid()
     plt.xlabel('Test Filesize')
     plt.ylabel('Accuracy')
-    plt.legend(title='Trained file sizes (mean c-rate)')
+    plt.legend(title='Trained file sizes (mean c-rate)', loc='upper left', bbox_to_anchor=(1, 1))
+    plt.gcf().set_size_inches(9, 5)
+    # Use tight_layout to ensure all elements fit within the saved area
+    plt.tight_layout()
     plt.savefig('Plots/accuracy/accuracy_comparison_filtered.pgf')
     plt.close()
 
@@ -264,26 +274,6 @@ def plot_loss_results():
         plt.savefig('Plots/loss_comparison/loss_comparison_fs_' + filesize + '_model.pgf')
         plt.close()
 
-def plot_dec_enc_time():
-    exec_time_dict = {
[…]

### 2024-01-14 scripts/plotResults.py
add pgf with no crop

@@ -294,6 +294,9 @@ def plot_filesize_to_target():
     plt.xlabel('Codec')
     plt.ylabel('Filesize (KB)')
     plt.xticks(rotation=45)
+    plt.gcf().set_size_inches(7, 6)
+    # Use tight_layout to ensure all elements fit within the saved area
+    plt.tight_layout()
     plt.savefig('Plots/filesize_to_target.pgf')
     plt.close()
 

### 2024-01-14 Paper/main.tex
fix figure
change resNet to ResNet-18

@@
 
-\subsection{Evaluation of ResNet Performance Without Transfer Learning} 
-Prior to the implementation of transfer learning methodologies, an analysis was conducted to ascertain whether the selected ResNet architecture could independently identify various image compression algorithms.
+\subsection{Evaluation of ResNet-18 Performance Without Transfer Learning} 
+Prior to the implementation of transfer learning methodologies, an analysis was conducted to ascertain whether the ResNet-18 architecture could independently identify various image compression algorithms.
 The entire dataset of one specific compression size, was processed through the model, and the outputs were L2 normalized.
@@
 	\centering
-	\includegraphics[width=\textwidth]{Plots/plot_scatter_without_transfer_10.pgf}
-	\caption{10kB Compression: ResNet without transfer learning}
+	\resizebox{\textwidth}{!}{\input{../Plots/plot_scatter_without_transfer_10.pgf}}
+    \caption{Archived filesizes for used encoder}
 	\label{fig: no_transfer}

### 2024-01-14 scripts/quality.py
Add second psnr and ssim plot with adapted limits (#97)

@@ -13,7 +13,8 @@ pillow_heif.register_heif_opener()
 import cv2
 import matplotlib.pyplot as plt
 import matplotlib
-#Make matplotlib use latex for font rendering
+
+# Make matplotlib use latex for font rendering
 matplotlib.use("pgf")
 matplotlib.rcParams.update({
     "pgf.texsystem": "pdflatex",
@@ -180,7 +181,7 @@ def measure_quality(useMultiCropPerImage=False):
     np.save('results/results_quality.npy', results)
 
 
-def _plot_results(codecs, results, metric, save_path):
+def _plot_results(codecs, results, metric, save_path, x_lim, y_lim_psnr, y_lim_ssim):
     plt.rc('font', size=23)
     plt.figure(figsize=(13, 13))
 
@@ -192,11 +193,13 @@ def _plot_results(codecs, results, metric, save_path):
 
     plt.legend()
     if metric == 'PSNR':
-        plt.ylim((28, 45))
-    plt.xlim((4, 100))
+        plt.ylim(y_lim_psnr)
+    elif metric == 'SSIM' and y_lim_ssim:
+        plt.ylim(y_lim_ssim)
+    plt.xlim(x_lim)
     plt.xlabel('Compression Rate')
     plt.ylabel(metric)
-    plt.savefig(save_path+'.pgf')
+    plt.savefig(save_path + '.pgf')
     plt.close()
 
 
@@ -209,9 +212,11 @@ def plot_results():
     ssim_sub_dict = {key: [results[key][0], results[key][2]] for key in codecs}
     time_sub_dict = {key: [results[key][0], results[key][3]] for key in codecs}
 
-    _plot_results(codecs, psnr_sub_dict, 'PSNR', 'Plots/psnr.pgf')
-    _plot_results(codecs, ssim_sub_dict, 'SSIM', 'Plots/ssim.pgf')
-    _plot_results(codecs, time_sub_dict, 'Time (ms)', 'Plots/enc_time.pgf')
+    _plot_results(codecs, psnr_sub_dict, 'PSNR', 'Plots/psnr.pgf', (4, 100), (28, 45), None)
+    _plot_results(codecs, ssim_sub_dict, 'SSIM', 'Plots/ssim.pgf', (4, 100), None, None)
+    _plot_results(codecs, psnr_sub_dict, 'PSNR', 'Plots/psnr_adapted.pgf', (10, 100), (28, 38), None)
[…]

### 2024-01-14 scripts/plotResults.py
add accuracy plot without mixed models (#96)
* add accuracy plot without mixed models

* Adapt legend alignment

---------

Co-authored-by: Michael Hafner <hafneer@gmail.com>

@@ -62,10 +62,32 @@ def plot_accuracy_results():
     plt.grid()
     plt.xlabel('Test Filesize')
     plt.ylabel('Accuracy')
-    plt.legend(title='Trained file sizes (mean c-rate)')
+    plt.legend(title='Trained file sizes (mean c-rate)', loc='upper left', bbox_to_anchor=(1, 1))
+    plt.gcf().set_size_inches(9, 5)
+    # Use tight_layout to ensure all elements fit within the saved area
+    plt.tight_layout()
     plt.savefig('Plots/accuracy/accuracy_comparison.pgf')
     plt.close()
 
+    # plot accuracy without mixed models
+    set_figsize()
+    for filesize in filesizes:
+        res_dict = np.load(RESULTS_FOLDER + 'accuracy_fs_' + filesize + '_model.npy', allow_pickle=True).item()
+        keys = [int(key) for key in res_dict.keys()]
+        plt.plot(keys, res_dict.values(), color=color_dict[filesize],
+                 label=filesize + f'  c-rate: {(AVG_FILESIZE / float(filesize)):.2f}')
+
+    plt.grid()
+    plt.xlabel('Test Filesize')
+    plt.ylabel('Accuracy')
+    plt.legend(title='Trained file sizes (mean c-rate)', loc='upper left', bbox_to_anchor=(1, 1))
+    plt.gcf().set_size_inches(9, 5)
+    # Use tight_layout to ensure all elements fit within the saved area
+    plt.tight_layout()
+    plt.savefig('Plots/accuracy/accuracy_comparison_withoutMixed.pgf')
+    plt.close()
+
+    # plot filtered accuracy
     filesizes = ['10', '25', '40', '100']
 
     # load dic from file
@@ -88,7 +110,10 @@ def plot_accuracy_results():
     plt.grid()
     plt.xlabel('Test Filesize')
     plt.ylabel('Accuracy')
-    plt.legend(title='Trained file sizes (mean c-rate)')
+    plt.legend(title='Trained file sizes (mean c-rate)', loc='upper left', bbox_to_anchor=(1, 1))
+    plt.gcf().set_size_inches(9, 5)
+    # Use tight_layout to ensure all elements fit within the saved area
+    plt.tight_layout()
     plt.savefig('Plots/accuracy/accuracy_comparison_filtered.pgf')
     plt.close()
 
@@ -249,26 +274,6 @@ def plot_loss_results():
[…]

### 2024-01-14 scripts/plotResults.py
fix JXR 1 compressing to 10 kb & add JXR2 (#98)
* fix JXR 1 compressing to 10 kb & add JXR2

* include all plots again

* add pdf

* add pgf with no crop

@@ -295,10 +295,13 @@ def plot_filesize_to_target():
     plt.axhline(y=32, color='green', linestyle='--', label='Target')
     # legend
     plt.legend(title='Codec')
-    plt.title('Actual Filesize to Target Comparison')
     plt.grid()
     plt.xlabel('Codec')
     plt.ylabel('Filesize (KB)')
+    plt.xticks(rotation=45)
+    plt.gcf().set_size_inches(7, 6)
+    # Use tight_layout to ensure all elements fit within the saved area
+    plt.tight_layout()
     plt.savefig('Plots/filesize_to_target.pgf')
     plt.close()
 

### 2024-01-24 Paper/main.tex
add new images to paper
add images to paper
add packages and change importname of the last plot

@@
 \documentclass{article}
+\usepackage{tikz}
+\usepackage{tikz-cd}
+\usepackage{pgfplots}
 \usepackage[a4paper, margin=1in]{geometry}
@@
 
+\begin{figure}[h!]
+    \centering
+      \begin{subfigure}{0.49\textwidth}
+        \resizebox{\textwidth}{!}{\input{../Plots/psnr_adapted.pgf}}
+          \caption{PSNR comparison of the used codecs}
+          \label{fig: psnr_comparison}
+      \end{subfigure}
+      \hfill
+      \begin{subfigure}{0.49\textwidth}
+        \resizebox{\textwidth}{!}{\input{../Plots/ssim_adapted.pgf}}
+          \caption{SSIM comparison of the used codecs}
+          \label{fig:CI}
+      \end{subfigure}
+\caption{
+\label{fig: comparison}%
+Comparison of PSNR and SSIM}
+\end{figure}
+
 \noindent
@@
 
+\begin{figure}[h!]
+	\centering
+	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison_filtered.pgf}}
+	\caption{Accuracy Comparison}
+	\label{fig: acc_comparison}
+\end{figure}
+
+\begin{figure}[h!]
+	\centering
+	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison_withoutMixed.pgf}}
+	\caption{Accuracy Comparison}
+	\label{fig: acc_comparison}
+\end{figure}
+
 \noindent
@@
          \centering
-        \resizebox{\textwidth}{!}{\input{../Plots/loss_comparison/loss_comparison_fs_mixed_model.pgf}}
+         \resizebox{\textwidth}{!}{\input{../Plots/loss_comparison/loss_comparison_mixed_model.pgf}}
          \caption{Loss of mixed model}

### 2024-01-30 scripts/cnnDataset.py
add model with files sizes 5 - 100

@@ -5,12 +5,14 @@ from torchvision import transforms
 # ImageFile.LOAD_TRUNCATED_IMAGES = True
 
 # create a training and test dataset
+
+
 def create_dataset(transform=transforms.ToTensor(), filesize="all"):
     # create a training dataset from multiple image folders 'Images/DIV2K_train_HR'
     trainset = torchvision.datasets.ImageFolder(root='Images/DIV2K_train_HR/Decoded/'+filesize+'/', transform=transform)
     # target_transform = Lambda(lambda y: torch.zeros(10, dtype=torch.float).scatter_(dim=0, index=torch.tensor(y), value=1))
     # create a test dataset from multiple image folders 'Images/DIV2K_valid_HR'
     testset = torchvision.datasets.ImageFolder(root='Images/DIV2K_valid_HR/Decoded/'+filesize+'/', transform=transform)
-    trainloader = torch.utils.data.DataLoader(trainset, batch_size=1, shuffle=True)
-    testloader = torch.utils.data.DataLoader(testset, batch_size=1, shuffle=False)
+    trainloader = torch.utils.data.DataLoader(trainset, batch_size=32, shuffle=True)
+    testloader = torch.utils.data.DataLoader(testset, batch_size=32, shuffle=False)
     return trainloader, testloader

### 2024-01-30 scripts/preprocessingAll.py

@@ -22,26 +22,26 @@ async def preprocess(cropNeeded=False,
         # first crop images
         print('Start to crop images to {}x{} pixel.'.format(width, height))
         cropImages.crop(width, height)
-        
+
     filesizes = [5, 10, 17, 25, 32, 40, 50, 60, 75, 100]
     for maxFileSizeKb in filesizes:
         # start the encoding and decoding task of each codec asynchronously
         print('Start to encode images. Filesize='+str(maxFileSizeKb))
         with ThreadPoolExecutor() as executor:
             futures = [
-                executor.submit(avifenc.encode_avif, printProgress, maxFileSizeKb),  
-                executor.submit(bpgenc.encode_bpg, printProgress, maxFileSizeKb),     
-                executor.submit(heicEnc.encode_heic, printProgress, maxFileSizeKb),   
-                executor.submit(jpegenc.encode_jpeg, printProgress, maxFileSizeKb),   
-                executor.submit(jpeg2000enc.encode_jpeg2k, printProgress, maxFileSizeKb), 
-                executor.submit(jpegxl.encode_jpgxl, printProgress, maxFileSizeKb),   
-                executor.submit(jxrenc_0.encode_jxr, printProgress, maxFileSizeKb),   
-                executor.submit(jxrenc_1.encode_jxr, printProgress, maxFileSizeKb),   
-                executor.submit(jxrenc_2.encode_jxr, printProgress, maxFileSizeKb),   
+                executor.submit(avifenc.encode_avif, printProgress, maxFileSizeKb),
+                executor.submit(bpgenc.encode_bpg, printProgress, maxFileSizeKb),
+                executor.submit(heicEnc.encode_heic, printProgress, maxFileSizeKb),
+                executor.submit(jpegenc.encode_jpeg, printProgress, maxFileSizeKb),
+                executor.submit(jpeg2000enc.encode_jpeg2k, printProgress, maxFileSizeKb),
+                executor.submit(jpegxl.encode_jpgxl, printProgress, maxFileSizeKb),
+                executor.submit(jxrenc_0.encode_jxr, printProgress, maxFileSizeKb),
                 executor.submit(webP.encode_webp, printProgress, maxFileSizeKb),
             ]
             for future in futures:
                 future.result()
+        jxrenc_1.encode_jxr(printProgress, maxFileSizeKb)
+        jxrenc_2.encode_jxr(printProgress, maxFileSizeKb)
         print('Finished preprocessing job.')
 
 

### 2024-01-30 scripts/plotResults.py
Adapt plots where mixed all is present

@@ -27,6 +27,7 @@ def plot_accuracy_results():
 
     # load dic from file
     mixed_results = np.load(RESULTS_FOLDER + 'accuracy_mixed_model.npy', allow_pickle=True).item()
+    mixed_results_all = np.load(RESULTS_FOLDER + 'accuracy_fs_all_model.npy', allow_pickle=True).item()
     keys = [int(key) for key in mixed_results.keys()]
 
     # Map file sizes to colors
@@ -47,7 +48,8 @@ def plot_accuracy_results():
 
     cmap = plt.get_cmap('tab20')
     set_figsize()
-    plt.plot(keys, mixed_results.values(), color=cmap(0), label='Mixed pre trained (5-32)')
+    plt.plot(keys, mixed_results.values(), color=cmap(1), label='Mixed pre trained (5-32)')
+    plt.plot(keys, mixed_results_all.values(), color=cmap(0), label='Mixed pre trained (5-100)')
      
     mixed_self_results = np.load(RESULTS_FOLDER + 'accuracy_mixed_self_model.npy', allow_pickle=True).item()
     keys = [int(key) for key in mixed_self_results.keys()]
@@ -95,7 +97,7 @@ def plot_accuracy_results():
     keys = [int(key) for key in mixed_results.keys()]
     cmap = plt.get_cmap('tab20')
     set_figsize()
-    plt.plot(keys, mixed_results.values(), color=color_dict['pre'], label='Mixed pre trained (5-32)')
+    plt.plot(keys, mixed_results_all.values(), color=color_dict['pre'], label='Mixed pre trained (5-100)')
 
     mixed_self_results = np.load(RESULTS_FOLDER + 'accuracy_mixed_self_model.npy', allow_pickle=True).item()
     keys = [int(key) for key in mixed_self_results.keys()]

### 2024-01-30 Paper/main.tex
Adapt plots where mixed all is present
make changes in paper

@@
 Therefore, each image of the dataset was cropped into five images to get an amount of 4500 images for the training and testing.
+For the purpose of comparison, an additional model was trained using images all available filesizes 5, 10, 17, 25, 32, 40, 50, 60, 75 and 100.
+This particular model utilized 9000 images during the training phase.
 
@@
 \section{Performance}
-For the classification each model was evaluated with each filesize. The result is represented in the figure \ref{fig: acc_comparison}.
+For the classification each model was evaluated with each filesize. The result is represented in the figure \ref{fig: acc_comparison all}.
 
@@
 	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison.pgf}}
-	\caption{Accuracy Comparison}
-	\label{fig: acc_comparison}
+	\caption{Accuracy Comparison All Models}
+	\label{fig: acc_comparison all}
 \end{figure}
@@
 	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison_filtered.pgf}}
-	\caption{Accuracy Comparison}
-	\label{fig: acc_comparison}
+	\caption{Accuracy Comparison Subset of Models}
+	\label{fig: acc_comparison filtered}
 \end{figure}
@@
 	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison_withoutMixed.pgf}}
-	\caption{Accuracy Comparison}
-	\label{fig: acc_comparison}
+	\caption{Accuracy Comparison of Filesize Models}
+	\label{fig: acc_comparison filesize}
 \end{figure}
@@
 This leads to 4000 images for each codec per epoch.
-As one can see in figure \ref{fig: acc_comparison} the self trained model has its best performances at filesizes 10, 17 and 25 ranging from 62 to 65 percent accuracy.
+As one can see in figure \ref{fig: acc_comparison all} the self trained model has its best performances at filesizes 10, 17 and 25 ranging from 62 to 65 percent accuracy.
 
@@
 \noindent
-An assumtion was that the mixed model would lead to the best result because of considering different filesizes for the model.
-As the figure \ref{fig: acc_comparison} shows, almost every small filesize model has a better performance than the mixed model.
-
-\noindent
-For classifying images with the given filesizes the model trained with 40kB would lead to the best result.
-However, for smaller filesize images (\textless 50kB) the model trained with 32kB images would be the right choice because of the bigger accuracy for 5kB images.
+An assumption was that the mixed model would lead to the best result because of considering different filesizes for the model.
+This assumption got proven by the mixed pre trained model (5-100), shown in the figure \ref{fig:loss_comparison_filesize_10}.
 

### 2024-01-31 Paper/main.tex
Adapt learned images in paper
make changes in paper

@@
 \noindent
-In the first iteration we trained the network on the original cropped 800 images per class.
+In the first iteration we trained the network on the original cropped 800 images per class for a filesize of 32kB.
 This leads to 8000 images available for the network to train.
 With that amount there was little progress during the first epochs.
-To be able to train on a larger dataset we then cropped the corners of each image to 512x512 to get 5x the number of usable images.
-This lead to 4000 images per class for the network to train.
-
 \noindent
-After 10 epochs of training, we achieved a validation accuracy of 57,6 percent avaged over the 5 training filesizes (5, 10, 17, 25 and 32).
+After 10 epochs of training, we achieved a validation accuracy of 57,6 percent averaged over the 5 training filesizes (5, 10, 17, 25 and 32).
 For 10 epochs this is lower than the results we got for the transfer learning approach.
@@
 \noindent
-Then the model was trained over 10 epochs on 4000 test images.
+Then the models were trained over 10 epochs on 40000 and evaluated on 5000 images.
 The learning rate was set to 0.001 with a momentum of 0.9 due to the model being already trained on a huge data set and in the experiment just the adjustment for the codec artifacts should be added.
@@
 \label{Results}
-A mixed model was developed by training the model with images of filesizes 5, 10, 17, 25 and 32.
-This resulted in 4500 images (512x512) for each codec.
+A mixed model was developed by training and evaluating the model with images of filesizes 5, 10, 17, 25 and 32.
+This resulted in 4500 (800 images per filesize and codec * 5 filesizes for training and 100 * 5 for validation) images (512x512) for each codec.
 The considered dataset has only 900 images.
 To compare the filesize models with the mixed model, the filesize models need the same amount of input images as the mixed model.
-Therefore, each image of the dataset was cropped into five images to get an amount of 4500 images for the training and testing.
+Therefore, each image of the dataset was cropped into five images to get an amount of 4500 (800 images per filesize and codec * 5 images cropped from one for training and 100 * 5 for validation) images for training and validation.
 For the purpose of comparison, an additional model was trained using images all available filesizes 5, 10, 17, 25, 32, 40, 50, 60, 75 and 100.
-This particular model utilized 9000 images during the training phase.
+This particular model utilized 80000 images during the training.
 

### 2024-01-31 scripts/quality.py
Add images to paper (#100)
* add new images to paper

* Add acc_comparison plot without mixed model

* add images to paper

* fix scatter plot

* add packages and change importname of the last plot

* change label of JPEG XR

* Adapt quality legend

* add model with files sizes 5 - 100

* Adapt plots where mixed all is present

* make changes in paper

* Adapt learned images in paper

* make changes in paper

---------

Co-authored-by: Michael Hafner <hafneer@gmail.com>
Co-authored-by: Stefan Findenig <s.findenig@gmail.com>
Co-authored-by: aleksandarRa <radovic.aleksandar@gmx.at>

@@ -182,6 +182,19 @@ def measure_quality(useMultiCropPerImage=False):
 
 
 def _plot_results(codecs, results, metric, save_path, x_lim, y_lim_psnr, y_lim_ssim):
+    codec_mapping = {
+        'avif': "AVIF",
+        'webP': "WEBP",
+        'bpg': "BPG",
+        'heic': "HEIC",
+        'jxl': "JPEG XL",
+        'jxr_0': "JPEG XR_0",
+        'jxr_1': "JPEG XR_1",
+        'jxr_2': "JPEG XR_2",
+        'jpeg': "JPEG",
+        'jpeg2000': "JPEG 2000"
+    }
+
     plt.rc('font', size=23)
     plt.figure(figsize=(13, 13))
 
@@ -189,7 +202,7 @@ def _plot_results(codecs, results, metric, save_path, x_lim, y_lim_psnr, y_lim_s
         codec_results = results[codec]
         mean_crates = codec_results[0]
         mean_metric = codec_results[1]
-        plt.plot(mean_crates, mean_metric, label=codec)
+        plt.plot(mean_crates, mean_metric, label=codec_mapping[codec])
 
     plt.legend()
     if metric == 'PSNR':
@@ -222,4 +235,4 @@ def plot_results():
 if __name__ == '__main__':
     measure_quality()
     plot_results()
-    print('Quality measurement successful.')
+    print('Qu/home/michael/Documents/AIS/3_semester/FH/NLP/Applied/UNI-FH-Applied-NLP-CoLaality measurement successful.')

### 2024-02-01 scripts/quality.py
Adapt quality and time plots

@@ -194,17 +194,30 @@ def _plot_results(codecs, results, metric, save_path, x_lim, y_lim_psnr, y_lim_s
         'jpeg': "JPEG",
         'jpeg2000': "JPEG 2000"
     }
+    jxr_parameter = ["q (0.0-1.0)", "q (2-255)"]
 
-    plt.rc('font', size=23)
-    plt.figure(figsize=(13, 13))
+    set_figsize()
 
+    cmap = plt.get_cmap('tab20')
+    index = 0
     for codec in codecs:
         codec_results = results[codec]
         mean_crates = codec_results[0]
         mean_metric = codec_results[1]
-        plt.plot(mean_crates, mean_metric, label=codec_mapping[codec])
+        if "jxr" in codec:
+            for measure in jxr_parameter:
+                metric_subset = mean_metric[:25] if "." in measure else mean_metric[25:]
+                crates_subset = mean_crates[:25] if "." in measure else mean_crates[25:]
+                plt.plot(crates_subset, metric_subset, label=codec_mapping[codec] + "  " + measure, color=cmap(index))
+                index += 1
+            continue
+        plt.plot(mean_crates, mean_metric, label=codec_mapping[codec], color=cmap(index))
+        index += 1
 
-    plt.legend()
+    plt.legend(title='Codecs (quality parameter)', loc='upper left', bbox_to_anchor=(1, 1))
+    plt.gcf().set_size_inches(9, 5)
+    # Use tight_layout to ensure all elements fit within the saved area
+    plt.tight_layout()
     if metric == 'PSNR':
         plt.ylim(y_lim_psnr)
     elif metric == 'SSIM' and y_lim_ssim:
@@ -232,7 +245,10 @@ def plot_results():
     _plot_results(codecs, time_sub_dict, 'Time (ms)', 'Plots/enc_time.pgf', (4, 100), None, None)
 
 
+def set_figsize():
+    plt.figure(figsize=(7, 5))
+    plt.rcParams['font.size'] = 12
+
 if __name__ == '__main__':
     measure_quality()
     plot_results()
-    print('Qu/home/michael/Documents/AIS/3_semester/FH/NLP/Applied/UNI-FH-Applied-NLP-CoLaality measurement successful.')
